### 2022-03-06 R/Paper_plots_lenticel_damage.Rmd
R files

---
title: "Paper_Cartama_lenticel_damage"
author: "dru"
date: "2/3/2022"
output:
  pdf_document: default
  html_document: default
---

## Preparing the environment

Loading required Packages

```{r Packages, echo=TRUE, message=FALSE, warning=FALSE}
library(tidyverse)
library(gridExtra)
library(readxl)
library(ggpubr)
library(tibble)
library(ggplot2)
library(extrafont)
loadfonts(device = "win")

```

## Loading and inspecting the data

Loading and inspecting the file 'Lenticel_Damage_Summary_All_Harvest.xlsx'. This file has two-years of lenticel damage measurements recorded in two avocado farms across four harvest.

```{r echo=TRUE, message=FALSE, warning=FALSE}
Lenticel_file <- read_excel("C:/Users/Dru/Desktop/Paper_Aguacate/Lenticel_Damage_Summary_All_Harvest.xlsx")
glimpse(Lenticel_file)
```
Checking for NA, miss speels and anomalies in the data:

```{r inspecting}

table(Lenticel_file$Cosecha)
table(Lenticel_file$UP)

f <-subset(Lenticel_file,Lenticel_file$UP=="Escondida")
f1 <- subset(Lenticel_file,Lenticel_file$UP=="Sinai")
table(f$Lote)
table(f$Arbol)
table(f1$Lote)
table(f1$Arbol)
summary(Lenticel_file$Severidad_0)
summary(Lenticel_file$Severidad_1)
summary(Lenticel_file$Incidencia_0)
summary(Lenticel_file$Incidencia_1)

```
Problems:

* Some tree numbers are shared between La Escondida y El Sinai, and this redundancy can result in problems during the analysis.
* Lenticel damage columns have several NA. Fruits having NA the severidad_0 or incidence_0 were removed from all the analyses, and those having NA in severidad_1 or incidence_1 only from the analysis evaluating disease progresion

## Cleaning and preparing the data
### cleaning actions:

* The columns cosecha, Año, Severidad_pedunculo,Fruta and the last three empty columns were removed as they are not used during the analysis
* The 'p' simbol in the column Cosecha is changed for 'm' to especify the main harvest.
* Generated a column Tree which has the name of the tree indicated by the farm and tree number (i.e., Sinai15) to avoid problems during the analysis
* Removed the Arbol and Fruta columns

```{r cleaning}
Lenticel_file$...13<-NULL
Lenticel_file$...14<-NULL
Lenticel_file$...15<-NULL
Lenticel_file$Año<-NULL
Lenticel_file$cosecha<-NULL
Lenticel_file$Fruta<-NULL
Lenticel_file$Severidad_pedunculo<-NULL
Lenticel_file[Lenticel_file=="2019_p"]<-"2019_m"
Lenticel_file[Lenticel_file=="2020_p"]<-"2020_m"
Lenticel_file$Tree<-paste(Lenticel_file$UP,Lenticel_file$Arbol,sep="")
Lenticel_file$Arbol<-NULL

df <- Lenticel_file %>% drop_na(Severidad_0 , Incidencia_0)
colnames(df)[which(names(df) == "Cosecha")] <- "Harvest"
colnames(df)[which(names(df) == "UP")] <- "Farm"
colnames(df)[which(names(df) == "Lote")] <- "Plot"
colnames(df)[which(names(df) == "Severidad_0")] <- "Sev_0dph"
colnames(df)[which(names(df) == "Severidad_1")] <- "Sev_21dph"
colnames(df)[which(names(df) == "Incidencia_0")] <- "Inc_0dph"
colnames(df)[which(names(df) == "Incidencia_1")] <- "Inc_21dph"
glimpse(df)
summary(df$Sev_0dph)

```
## Processing and plottin the lenticel damage data at 0 dph for the farms and harvest

* The mean of the severity and incidence of the lenticel damage was calculated grouping by Plot and Harvest

```{r df_for_barplot}

df_mean <- tapply(df$Sev_0dph , list(df$Plot , df$Harvest) , mean)
sev <- df_mean[1 , ]
df_mean1 <- tapply(df$Inc_0dph , list(df$Plot , df$Harvest) , mean)
inc <- df_mean1[1 , ]

for (i in 2:13){
  sev<-c(sev , df_mean[i,])
  inc <- c(inc , df_mean1[i,])
  }
mat <- data.frame(rep(c("2019_m" , "2020_m" , "2020_t" , "2021_t") , 13) , c(rep("Escondida" , 24) , rep("Sinai" , 28)) , sev , inc)

colnames(mat) <- c("Harvest" , "Farm" , "Severity" , "Incidence")

print(head(mat))

```
* The barplot showing the severity of lenticel damage for the farms across harvest Harvest. The bars and error bars represent the severity mean and standard deviation observed in the farms for each harvest at 0 dph, and the points represent the severity mean for the plots in the farm.

```{r severity plot}

p <-  ggplot(mat, aes(x = factor(Harvest,levels = c("2019_m","2020_t","2020_m","2021_t")), y = Severity)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(), fill=rep(c("gray90","gray70"),4),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
p <- p + geom_jitter()+ facet_wrap(~Farm) + theme_classic() 
p <- p +  xlab("") + ylab("Necrotic Area (%)")
p <- p + theme(axis.title =element_text(size=14,family = 'serif'))
p <- p +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
p <- p + theme(strip.text.x = element_text(size = 14,family = 'serif'))

```

* The barplot showing the Incidence of lenticel damage for the farms across harvest Harvest. The bars and error bars represent the severity mean and standard deviation observed in the farms for each harvest at 0 dph, and the points represent the incidence mean for the plots in the farm.

```{r Incidence plot}

p1 <-  ggplot(mat, aes(x = factor(Harvest,levels = c("2019_m","2020_t","2020_m","2021_t")), y = Incidence)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(), fill=rep(c("gray90","gray70"),4),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
p1 <- p1 + geom_jitter()+ facet_wrap(~Farm) + theme_classic() 
p1 <- p1 +  xlab("") + ylab("Necrotic spots")
p1 <- p1 + theme(axis.title =element_text(size = 14 , family = 'serif'))
p1 <- p1 +  theme(axis.text.x = element_text(face="bold", size = 12, angle = 0 , family = 'serif'),
              axis.text.y = element_text(face = "bold" , size = 12 , angle = 0 , family = 'serif'))
p1 <- p1 + theme(strip.text.x = element_text(size = 14 , family = 'serif'))

```

* Fig 1.* Lenticel damage for avocado cv. Hass fruits collected from the La Escondida and El Sinai farms between 2019 and 2021 at harvest time (0 days post-harvest). Bars and errorbars represent mean and standard deviation for the severity (A) and incidence (B) of the damage observed in the farms for each harvest at 0 dph. The points show the severity and incidence means for the fruits collected from the different plots, and the letter after the year denotes main (m) and traviesa (t) harvest.

```{r severity and incidence plot}

 plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)

```

## Processing and plottin the lenticel damage increase between 0 dph and 21 dpc

* Note: The analisis omitted fruits with no record of lenticel damage (NA) at 21 dph
* were omitted from  was calculated grouping by Plot and Harvest

```{r df_for_barplot plots}

df1 <- na.omit(df)

sev <- c(df1$Sev_0dph , df1$Sev_21dph)
inc <- c(df1$Inc_0dph , df1$Inc_21dph)
farm <- c(df1$Farm , df1$Farm)
time <-factor(c(rep("0dpc",length(sev)/2) , rep("21dpc",length(sev)/2)))
harvest <- c(df1$Harvest , df1$Harvest)

mat <- data.frame(Farm = farm, Time = time , Harvest = harvest, Severity = sev , Incidence = inc)

mat_mean<-tapply(mat$Severity , list(mat$Time,mat$Harvest,mat$Farm),mean)
mat_mean1<-tapply(mat$Incidence , list(mat$Time,mat$Harvest,mat$Farm),mean)

mat1<-data.frame(Farm = c(rep("Escondida" , 8) , rep("Sinai" , 8)), Time = rep(c(rep("0dpc",4) , rep("21dpc",4)) , 2) ,
                 Harvest = rep(c("2019_m" , "2020_m" , "2020_t" , "2021_t") , 4), 
                 Severity = c(mat_mean[1,,1] , mat_mean[2,,1] , mat_mean[1,,2] , mat_mean[2,,2]),
                 Incidence = c(mat_mean1[1,,1] , mat_mean1[2,,1] , mat_mean1[1,,2] , mat_mean1[2,,2]) )

head(mat1)

```
* The barplot showing the increase in the severity of lenticel damage during the cold storage. The bars and error bars represent the severity mean and standard deviation observed in the farms at the two evaluations (0 dph and 21 dph), and the points represent the severity mean for the harvest in the farm.

```{r severity in time}
p <-  ggplot(mat1, aes(x = factor(Time), y = Severity)) + 
      geom_bar(stat="summary", color="black", positio=position_dodge(), fill= rep(c("gray95","gray85") ,2), fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
p <- p + geom_jitter(aes(colour = factor(Harvest , levels = c("2019_m" , "2020_t" , "2020_m" , "2021_t"))) , size = 2)
p <- p + facet_wrap(~ Farm) + theme_classic() 
p <- p +  xlab("") + ylab("Necrotic Area (%)")
p <- p + theme(axis.title =element_text(size=14,family = 'serif'))
p <- p +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
p <- p + theme(strip.text.x = element_text(size = 14,family = 'serif'))
p <- p + scale_color_manual(name = "Harvest", values =  rep(c("gray70","gray40") ,2))
p <- p + theme(legend.text = element_text(size=12, angle=0,family = 'serif'),
                legend.title = element_text(face="bold",size=12, angle=0,family = 'serif'))

```
* The barplot showing the increase in the Incidence of lenticel damage during the cold storage. The bars and error bars represent the incidence mean and standard deviation observed in the farms at the two evaluations (0 dph and 21 dph), and the points represent the severity mean for the harvest in the farm.

```{r incidence in time}
p1 <-  ggplot(mat1, aes(x = factor(Time), y = Incidence)) + 
      geom_bar(stat="summary", color="black", positio=position_dodge(), fill= rep(c("gray95","gray85") ,2), fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
p1 <- p1 + geom_jitter(aes(colour = factor(Harvest , levels = c("2019_m" , "2020_t" , "2020_m" , "2021_t"))) , size = 2)
p1 <- p1 + facet_wrap(~ Farm) + theme_classic() 
p1 <- p1 +  xlab("") + ylab("Necrotic spots")
p1 <- p1 + theme(axis.title =element_text(size=14,family = 'serif'))
p1 <- p1 +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
p1 <- p1 + theme(strip.text.x = element_text(size = 14,family = 'serif'))
p1 <- p1 + scale_color_manual(name = "Harvest", values =  rep(c("gray70","gray40") ,2))
p1 <- p1 + theme(legend.text = element_text(size=12, angle=0,family = 'serif'),
                legend.title = element_text(face="bold",size=12, angle=0,family = 'serif'))

```
*Fig 2.* Lenticel damage for avocado cv. Hass fruits collected from the La Escondida and El Sinai farms between 2019 and 2021 at harvest time (0 days post-harvest, 0 dph) and after 21 days of storage at 6C (21 days post-harvest, 21 dph). Shown are the means and standard deviations for the severity (A) and incidence (B) of the damage for the two evaluatin points (0 dph and 21 dph). The points show the severity and incidence means for the fruits collected in the four harvest, and the letter after the year denotes main (m) and traviesa (t) harvest.

```{r severity and incidence in time plot}

 plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)

```

### 2022-03-06 R/Paper_plots_microbial_ecology.Rmd
R files

---
title: "Paper_Cartama_Microbial_ecology"
author: "dru"
date: "2/16/2022"
output:
  pdf_document: default
  html_document: default
---

## Preparing the environment

Loading required Packages

```{r Packages}

library(tidyverse)
library(gridExtra)
library(tibble)
library(ggplot2)
library(extrafont)
loadfonts(device = "win")
library(phyloseq)
library(scales)   
library(ggpubr)
library(readxl)
library(vegan)
library(biomformat)

```

## Lenticel damage the fruits

Generating the dataframe containing the lenticel damage data for the differentialy diseased fruits used inthe microbial ecology annalisis

```{r data}

md <- data.frame("Severity"=c(.7 , .84 , 1.66 , 1.66 ,0.62 , 2.02 , 0.085 , 0.025 , 0.08 ,
                              0.085 ,0.095 , 0.285 , 23.4 , 17.97 , 15.99 , 19.13 , 19.01,
                              12.92 , 1.73 , 0.18 , 0.81 , 1.15 , 0.47 , 0.09),
                 "Incidence"=c(50 , 84 , 89 , 133 , 84 , 158 , 11 , 5 , 12 ,30 , 14 , 31 ,
                               525 , 488 , 347 , 269 , 358 , 515 , 128 , 62 ,119 , 94 ,
                               108 , 68),
                 "Farm"= c(rep("Escondida" , 12) , rep("Siani" , 12)),
                 "Damage"= c(rep(c(rep("Severe" , 6) , rep("Mild" , 6)),2)))

head(md)

```
Ploting the severity data:

```{r severity plot}

p <-  ggplot(md, aes(x = Damage, y = Severity)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(),
               fill=rep(c("gray90","gray70"),2),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2)
p <- p + geom_jitter()+ facet_wrap(~Farm) + theme_classic() 
p <- p +  xlab("") + ylab("Necrotic Area (%)")+ylim(c(0, max(md$Severity)*1.2))
p <- p + theme(axis.title =element_text(size=14,family = 'serif'))
p <- p +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
p <- p + theme(strip.text.x = element_text(size = 14,family = 'serif'))

p <- p +     geom_signif(test="t.test", comparisons = list(c("Severe", "Mild")), map_signif_level = T)

```
Ploting the incidence data:

```{r incidence plot}

p1 <-  ggplot(md, aes(x = Damage, y = Incidence)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(),
               fill=rep(c("gray90","gray70"),2),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
p1 <- p1 + geom_jitter()+ facet_wrap(~Farm) + theme_classic() 
p1 <- p1 +  xlab("") + ylab("Necrotic spots")+ylim(c(0, max(md$Incidence)*1.2))
p1 <- p1 + theme(axis.title =element_text(size=14,family = 'serif'))
p1 <- p1 +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
p1 <- p1 + theme(strip.text.x = element_text(size = 14,family = 'serif'))
p1 <- p1 +     geom_signif(test="t.test", comparisons = list(c("Severe", "Mild")), map_signif_level = T)
```
*Supplementary figure 3.* Lenticel damage for avocado cv. Hass fruits used for the microbial-community analysis. Fruits were collected from the La Escondida and El Sinai farms during the traviesa harvest of 2020. Shown are the means and standard deviations for the severity (A) and incidence (B) of the damage for the fruits with deferent levels of affection. The points show the severity and incidence for the fruits and the asterisk denote statistic differences at the 99.0% () and 99.9% () confidence level according to the t test (n: 6).

```{r severity and incidence plot}

 plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
```

## Alpha diversity plot

Loading the dataframe containing the alpha diversity metrics for the for the differentialy diseased fruits

```{r alfa df}
Alfa <- read_excel("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/Alfa/Alfa.xlsx")
head(Alfa)
```
Ploting the alpha_diversity metrics

```{r alpha-diversity plots}

#### Chao

c <-  ggplot(Alfa, aes(x = Damage_level, y = Chao)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(),
               fill=rep(c("gray90","gray70"),2),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar",
                   color="black", width=0.2) 
c <- c + geom_jitter()+ facet_wrap(~Farm)+ theme_classic() 
c <- c +  xlab("") + ylab("Chao")+ylim(c(0, max(Alfa$Chao)*1.1))
c <- c + theme(axis.title =element_text(size=14,family = 'serif'))
c <- c +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,
                                             family ='serif'),
                  axis.text.y = element_text(face="bold",size=12, angle=0,family =
                                               'serif'))
c <- c + theme(strip.text.x = element_text(size = 14,family = 'serif'))
c <- c + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)

#### Shannon_entropy

s <-  ggplot(Alfa, aes(x = Damage_level, y = Shannon_entropy)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(),
               fill=rep(c("gray90","gray70"),2),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar",
                   color="black", width=0.2) 
s <- s + geom_jitter()+ facet_wrap(~Farm)+ theme_classic() 
s <- s +  xlab("") + ylab("Shannon entropy")+ylim(c(0, max(Alfa$Shannon_entropy)*1.1))
s <- s + theme(axis.title =element_text(size=14,family = 'serif'))
s <- s +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,
                                             family ='serif'),
                  axis.text.y = element_text(face="bold",size=12, angle=0,family =
                                               'serif'))
s <- s + theme(strip.text.x = element_text(size = 14,family = 'serif'))
s <- s + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)

#### Riqueza

r <-  ggplot(Alfa, aes(x = Damage_level, y = Riqueza)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(),
               fill=rep(c("gray90","gray70"),2),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar",
                   color="black", width=0.2) 
r <- r + geom_jitter()+ facet_wrap(~Farm)+ theme_classic() 
r <- r +  xlab("") + ylab("Richness")+ylim(c(0, max(Alfa$Riqueza)*1.1))
r <- r + theme(axis.title =element_text(size=14,family = 'serif'))
r <- r +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,
                                             family ='serif'),
                  axis.text.y = element_text(face="bold",size=12, angle=0,family =
                                               'serif'))
r <- r + theme(strip.text.x = element_text(size = 14,family = 'serif'))
r <- r + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)

#### Faith_pd

f <-  ggplot(Alfa, aes(x = Damage_level, y = Faith_pd)) + 
      geom_bar(stat="summary", color="black", position=position_dodge(),
               fill=rep(c("gray90","gray70"),2),fun = mean) +
      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar",
                   color="black", width=0.2) 
f <- f + geom_jitter()+ facet_wrap(~Farm)+ theme_classic() 
f <- f +  xlab("") + ylab("Faith pd")+ylim(c(0, max(Alfa$Faith_pd)*1.1))
f <- f + theme(axis.title =element_text(size=14,family = 'serif'))
f <- f +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,
                                             family ='serif'),
                  axis.text.y = element_text(face="bold",size=12, angle=0,family =
                                               'serif'))
f <- f + theme(strip.text.x = element_text(size = 14,family = 'serif'))
f <- f + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)

```

*Figure 3.* Alfa diversity for the fungal communities of the avocado cv. Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida and El Sinai farms during the traviesa harvest of 2020. Shown are the means and standard deviations for the alfa diversity index richness (A), Shannon (B), and Faith (C) alpha-diversity and the asterisk denote statistic differences at the 99.0% () and 99.9% () confidence level according to the t test (n: 6).

```{r severity and incidence plot}

 alpha_plot<-grid.arrange(r + labs(tag = 'A'),s + labs(tag = 'B'), f + labs(tag = 'C'), ncol=3,nrow=1)
```

## Beta diversity plots
Loading the ASVs table after CCS normalization and the phylogenetic tree for the Beta diversity annalysis

```{r uploading the CCS.biom and tree.nwk}
biomfile <- import_biom("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/css_eff.biom")
biomfile_mapfile <- import_qiime_sample_data("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/metadata_real.txt")
biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
sam <-sample_data(biomfile_merged)

otu.table <- otu_table(biomfile_merged)
taxa <- tax_table(biomfile_merged)

tree <- read_tree("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/tree.nwk")

otutax = phyloseq(otu.table, taxa)
merge2 = merge_phyloseq(otutax, sam, tree)
```

###PCoA

```{r PCoA}

example.ord <- ordinate(merge2, "PCoA", "Unifrac", weighted=TRUE)

PCoA<- plot_ordination(merge2, example.ord, type = "sites", color = "Farm", label = NULL)
PCoA = PCoA  + 
  geom_point(aes(color =Farm,shape = Farm1), size = 3) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        rect = element_rect(fill = "white", colour = "black",size = 0.5, linetype = 1),
        axis.ticks = element_line(colour = "black"),
        axis.title.x = element_text(face="plain",family = "serif", colour="black", size=12),
        axis.title.y = element_text(face="plain",family = "serif", colour="black", size=12),
        axis.text.x  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
        axis.text.y  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
        panel.background = element_rect(fill = "white", colour = "black", linetype = 1, size = 0.5),
        panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=11,family = "serif"), plot.margin = margin(1, 0.6, 1, 1, "cm"))  +
  scale_colour_manual(values=c("gray85","gray65","gray85","gray65"),labels = c("Escondida_Mild","Escondida_Severe", "Sinai_Mild","Sinai_Severe"))+  
  stat_ellipse(type = "t", size=0.5) + theme(legend.position = "bottom") +
  labs(x = "PCoA (60.4%)", y= "PCoA (12.2%)")
legend <- get_legend(PCoA)
PCoA <- PCoA + theme(legend.position="none")

```

###CAP

```{r CAP}
agricultural.ord<- ordinate(merge2, "CAP", "wunifrac", ~Farm)

agricultural_plot<- plot_ordination(merge2, agricultural.ord, type = "sites",
                                    color = "Farm",
                                    title = "", label = NULL)

CAP = agricultural_plot  +
  geom_point(aes(color =Farm,shape = Farm1), size = 3) +
  theme(panel.grid.major = element_blank(), 
        panel.grid.minor = element_blank(), 
        rect = element_rect(fill = "white", colour = "black",size = 0.5, linetype = 1),
        axis.ticks = element_line(colour = "black"),
        axis.title.x = element_text(face="plain",family = "serif", colour="black", size=12),
        axis.title.y = element_text(face="plain",family = "serif", colour="black", size=12),
        axis.text.x  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
        axis.text.y  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
        panel.background = element_rect(fill = "white", colour = "black", linetype = 1, size = 0.5),
        panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=11,family = "serif"), plot.margin = margin(0.71, 1, 1, 0.6, "cm"))  +
  scale_colour_manual(values=c("gray85","gray65","gray85","gray65"),labels =
                        c("Escondida_Mild","Escondida_Severe",
                          "Sinai_Mild","Sinai_Severe")) + 
  stat_ellipse(type = "t", size=0.5) + labs(x = "CAP (23.7%)", y= "CAP (45.8%)")+theme(legend.position = "none")

```
*Fig 4.* Fungal communities’ structure for fruits of avocado cv. Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida and El Sinai farms during the traviesa harvest of 2020. Cumulative sum scaling (CSS) transformed reads were used to calculate weighted unifrac distance. Shown are the bidimensional planes of the principal coordinates analysis (PCoA) (72.6 % of the overall variance) (A) and canonical analysis of principal coordinates (CAP) constrained by the farm (La Escondida and El Sinai) (68.8 % of the overall variance; p-value: 0.001) (B). Each point represents the fungal community of a fruit, and the colors show the origin (La Escondida o El Sinai) and damage severity (Severe or Mild) of the fruit. The ellipsis are the 95 % confidence level ellipses.

```{r PCoA and PCA plots}

po<-grid.arrange(PCoA+labs(tag = "A"),CAP+labs(tag = "B"),legend, ncol=2,nrow = 2, 
             layout_matrix = rbind(c(1,2), c(3,3)),
             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
```
## Taxonomy bat plots
Loading the ASVs table

```{r data barplot}
biomfile <- import_biom("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/ASVs_table9_dada2R.biom")
biomfile_mapfile <- import_qiime_sample_data("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/metadata_real.txt")
biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
#sample_data(biomfile_merged)

plot_colors <- c( "palegoldenrod","gray90", "plum4", "lightsteelblue","darkseagreen1",
                   "darkseagreen4","deepskyblue1","gray50" , "yellow2", "slateblue1",
                   "#CBD588", "#5F7FC7","#DA5724", "#508578", "#CD9BCD", "#AD6F3B",
                   "#673770","Khaki4", "#652926", "yellow3", "cadetblue3",
                   "lightsteelblue3", "honeydew3", "gray80","thistle4","yellow4",
                   "#5E738F", "#8A7C64","gray30", "lightpink3")
```

## Phylum barplot

```{r}
subset = biomfile_merged
rel.abun = transform_sample_counts(subset, function(x) x / sum(x))
glom <- tax_glom(rel.abun, taxrank = 'Phylum')
data_glom<- psmelt(glom) 
data_glom$Phylum <- as.character(data_glom$Phylum) 
data_glom$Phylum[data_glom$Abundance < 0.03] <- "< 3% abundancia"
data_glom$Phylum[data_glom$Phylum == "unidentified"] <- "Not classified"
data_glom$Phylum[data_glom$Phylum == "undefined"] <-"Not classified"

p1 <- ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Phylum, Abundance)))+
  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors) +
  ylab("Relative abundance") + xlab("") +
  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
        axis.line = element_line(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        axis.title.y = element_text(face="plain", colour="black", size=14,family="serif"),
        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=10,family="serif"),
        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif"),
        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.title = element_blank(),legend.text = element_text(family="serif",size=10)) + 
  theme(strip.text.x = element_text(size = 12 , family = 'serif'))

```

```{r Barplot Ascomycota }

subset = subset_taxa(biomfile_merged, Phylum == "Ascomycota")

rel.abun = transform_sample_counts(subset, function(x) x / sum(x) )
glom <- tax_glom(rel.abun, taxrank = 'Genus')
data_glom<- psmelt(glom)
data_glom$Genus <- as.character(data_glom$Genus)

data_glom$Genus[data_glom$Abundance < 0.03] <- "< 3% abundancia"
data_glom$Genus[data_glom$Genus == "unidentified"] <- "Not classified"
data_glom$Genus[data_glom$Genus == "undefined"] <-"Not classified"

p2<-ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Genus, Abundance)))+
  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors, name ="Genus") +
  ylab("Relative abundance") + xlab("") +
   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
        axis.line = element_line(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        axis.title.y = element_text(face="plain", colour="black", size=14,family="serif"),
        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=10,family="serif"),
        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif"),
        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.title = element_text(family="serif",size=12),legend.text = element_text(family="serif",size=10)) +
  theme(strip.text.x = element_text(size = 12 , family = 'serif'))

```

```{r Basidiomycota}
subset = subset_taxa(biomfile_merged, Phylum == "Basidiomycota")

rel.abun = transform_sample_counts(subset, function(x) x / sum(x) )
glom <- tax_glom(rel.abun, taxrank = 'Genus')
data_glom<- psmelt(glom)
data_glom$Genus <- as.character(data_glom$Genus)

data_glom$Genus[data_glom$Abundance < 0.03] <- "< 3% abundancia"
data_glom$Genus[data_glom$Genus == "unidentified"] <- "Not classified"
data_glom$Genus[data_glom$Genus == "undefined"] <-"Not classified"

p3<-ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Genus, Abundance)))+
  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors, name ="Genus") +
  ylab("Relative abundance") + xlab("")  +
    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
        axis.line = element_line(colour = "black"),
        axis.ticks = element_line(colour = "black"),
        axis.title.y = element_text(face="plain", colour="black", size=14,family="serif"),
        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=10,family="serif"),
        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif"),
        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
  theme(legend.title = element_text(family="serif",size=12),legend.text = element_text(family="serif",size=10)) +
  theme(strip.text.x = element_text(size = 12 , family = 'serif'))

```

```{r}
#po<-ggarrange(p1,ggarrange(p2, p3, nrow = 2), ncol = 2    , widths = c(0.78,1))

p1 <- p1 + theme(legend.key.height= unit(0.2, 'cm'),
        legend.key.width= unit(0.2, 'cm'))

p2 <- p2 + theme(legend.key.height= unit(0.2, 'cm'),
        legend.key.width= unit(0.2, 'cm'))

p3 <- p3 + theme(legend.key.height= unit(0.2, 'cm'),
        legend.key.width= unit(0.2, 'cm'))

po<-grid.arrange(p1+labs(tag= "A"),p3+labs(tag = "B"),p2+labs(tag = "C"), ncol=1,nrow = 3)

library(patchwork)
p2/p3 
```

### 2022-03-06 R/Funciones_lenticcelosis.R

@@ -1,0 +1,99 @@
+library(datasets)
+library(ggplot2)
+library(lme4)
+library(grid)
+library(gridExtra)
+
+
+###COMPRAR Y GUARDAR EL MODELO QE MEJOR EXPLIQUE EL SISTEMA
+###model_comparision(modelo mas complejo,modelo mas simple,nombre de archivo para guardar modelo)
+
+##y<-as.numeric(Datos_mat$Severidad_0)
+##modelo<-lmer(y~up + (1|ul)+(1|ula),REML = FALSE)
+###modelo1<-lmer(y~1 + (1|ul)+(1|ula),REML = FALSE)
+
+#### PE:model_comparision(modelo,modelo1,"/xx.txt")
+
+model_comparision<-function(a,b,saving_model){
+  
+  if (anova(a,b)$Pr[2]<0.05){
+    print("el modelo mas complejo fue guardado")
+    sink(saving_model)
+    print(summary(a))
+    sink() 
+  }else{
+    print("Me quedo con el modelo mas simple")
+    sink(saving_model)
+    
+    print(summary(b))
+    sink()}
+  return(anova(a,b)$Pr[2])
+}
+
+########Hacer el grafico boxplot
+######boxplot_por_lotes(Datos,factor (x),variable (y), grupos,orden_grupos,factores nombres (ejex),eje_x,eje_y,plot_title,limite menor eje y, limite mayor eje y, titulo legenda)
+#####plot1 <- boxplot_treatments(Datos_mat,Datos_mat$UP,Datos_mat$Severidad_0,Datos_mat$Cosecha,c("2019_p","2020_t","2020_p"),c("Escondida", "Sinai"),"","Severidad  (%)","",0,5,"Cosecha")
+
+boxplot_treatments<-function(Datos_mat,factor_x,variable_y,group,levels_order,names_x,eje_x,eje_y,plot_title,y_min,y_max,title_legend){
+  
+  
+  p<-ggplot(Datos_mat,aes(factor(factor_x),as.numeric(variable_y), color = factor(group, levels=levels_order)))
+  p<- p + geom_boxplot() + theme_classic() 
+  p<- p + geom_boxplot(outlier.colour="black", outlier.size=1)
+  p<- p + scale_x_discrete(limits=names_x)+labs(title=plot_title)
+  p<- p + theme(plot.title=element_text(size=18,face="bold",hjust = 0.5,family = 'Times'))
[…]

### 2022-03-06 R/Principal_lentcelosis.R

@@ -1,0 +1,207 @@
+#plot(residuals(modelo))
+#qqnorm(residuals(modelo))
+#plot(modelo)
+
+
+
+#############################################################################################
+###GENERACION Y LIMPIEZA DEL DATA SET #######################################################
+#############################################################################################
+
+
+Datos_mat<-resumencartamaseveridad
+Datos_mat$...13<-NULL
+
+Datos_mat$Incidencia_1<-NULL
+Datos_mat$Severidad_1<-NULL
+Datos_mat$Severidad_pedunculo<-NULL
+
+
+Datos_mat<-na.omit(Datos_mat)
+
+#Datos_mat<-subset(Datos_mat,Datos_mat$Cosecha!="2020_t")
+
+
+s_ped<-factor(Datos_mat$Severidad_pedunculo)
+lote<-factor(Datos_mat$Lote)
+arbol<-factor(Datos_mat$Arbol)
+up<-factor(Datos_mat$UP)
+ula<-up:lote:arbol
+ul<-up:lote
+la<- lote:arbol
+year<-factor(Datos_mat$Cosecha)
+fruta<-factor(Datos_mat$Fruta)
+
+
+################################################################################################
+############ MODELOS SEV E INC VS UP#########################################################
+################################################################################################
+
+
+y<-log(Datos_mat$Severidad_0+1)
+
+modelo<-lmer(y~up*year + (1|lote) + (1|la),REML = FALSE)
+modelo1<-lmer(y~up+year + (1|lote) + (1|la),REML = FALSE)
+modelo2<-lmer(y~1 +  + (1|lote) + (1|la),REML = FALSE)
+
+
+p_val<-model_comparision(modelo,modelo1,"Sev0_up.txt")
+
+y<-round(Datos_mat$Incidencia_0)
+
+modelo<-glmer(y~up*year + (1|lote) + (1|la),family = poisson)
+modelo1<-glmer(y~up+year + (1|lote) + (1|la),family = poisson)
+modelo2<-glmer(y~lote + (1|la),family = poisson)
+
+p_val<-model_comparision(modelo,modelo1,"Inc0_up.txt")
+
+y<-Datos_mat$Severidad_pedunculo
+
+modelo<-glm(y~up*year,family = quasipoisson)
+modelo1<-glm(y~up+year,family = quasipoisson)
[…]

### 2022-03-06 R/Principal_lentcelosis_plot.R

@@ -1,0 +1,247 @@
+
+
+# ###################### Plot sev e ind 0dp por lote o up#######################################
+
+  plot1 <- boxplot_treatments(Datos_mat,Datos_mat$UP,Datos_mat$Severidad_0,Datos_mat$Cosecha,c("2019_p","2020_t","2020_p","2021_t"),c("Escondida", "Sinai"),"","Severity  (%)","",0,5,"Harvest")
+  plot2 <- boxplot_treatments(Datos_mat,Datos_mat$UP,Datos_mat$Incidencia_0,Datos_mat$Cosecha,c("2019_p","2020_t","2020_p","2021_t"),c("Escondida", "Sinai"),"","Incidence","",0,350,"Harvest")
+#
+#
+ require(gridExtra)
+  plot<-grid.arrange(plot1,plot2, ncol=2,nrow=1)
+#
+  ggsave(plot,filename="Tiempo0_up.png",device="png", dpi=500, width = 28, height = 16, units = "cm")
+#
+#
+
+  plot1 <- boxplot_treatments(Datos_mat,Datos_mat$Lote,Datos_mat$Severidad_0,Datos_mat$Cosecha,c("2019_p","2020_t","2020_p","2021_t"),names(table(Datos_mat$Lote)),"","Severity  (%)","",0,15,"Harvest")
+  plot2 <- boxplot_treatments(Datos_mat,Datos_mat$Lote,Datos_mat$Incidencia_0,Datos_mat$Cosecha,c("2019_p","2020_t","2020_p","2021_t"),names(table(Datos_mat$Lote)),"","Incidence","",0,350,"Harvest")
+
+#
+ require(gridExtra)
+  plot<-grid.arrange(plot1,plot2, ncol=2,nrow=1)
+#
+ ggsave(plot,filename="Tiempo0_es.png",device="png", dpi=500, width = 28, height = 14, units = "cm")
+#
+#
+ plot<- stack_barplot(Datos_mat,Datos_mat$Severidad_pedunculo,Datos_mat$UP,c("sev","up","y"),c("3","2","1"),c("Escondida", "Sinai"),"","Proporci?n","Necrosis ped?nculo")
+#
+#  ggsave(plot,filename="Peduncle_up.png",device="png", dpi=500, width = 15, height = 15, units = "cm")
+
+
[…]

### 2022-03-07 R/Paper_plots_microbial_ecology.Rmd
dru

@@
 library(biomformat)
+library(patchwork)
+
+path<-"C:/Users/Dru/Desktop/Cartama_paper/files/MicrobialEcology"
 
@@
 ```{r alfa df}
-Alfa <- read_excel("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/Alfa/Alfa.xlsx")
+Alfa <- read_excel(paste(path,"/Alfa.xlsx",sep=""))
 head(Alfa)
@@
 ```{r uploading the CCS.biom and tree.nwk}
-biomfile <- import_biom("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/css_eff.biom")
-biomfile_mapfile <- import_qiime_sample_data("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/metadata_real.txt")
+biomfile <- import_biom(paste(path,"/css_eff.biom",sep=""))
+biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
 biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
@@
 
-tree <- read_tree("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/tree.nwk")
+tree <- read_tree(paste(path,"/tree.nwk",sep=""))
 
@@
 ```{r data barplot}
-biomfile <- import_biom("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/ASVs_table9_dada2R.biom")
-biomfile_mapfile <- import_qiime_sample_data("C:/Users/Dru/Desktop/microbial-ecology-avocado/Resultados_all/metadata_real.txt")
+biomfile <- import_biom(paste(path,"/ASVs_table9_dada2R.biom",sep=""))
+biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
 biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
@@
 
-library(patchwork)
 p2/p3 

### 2022-03-09 R/Paper_plots_lenticel_damage.Rmd
figures check

@@
 ```{r echo=TRUE, message=FALSE, warning=FALSE}
-Lenticel_file <- read_excel("C:/Users/Dru/Desktop/Paper_Aguacate/Lenticel_Damage_Summary_All_Harvest.xlsx")
+Lenticel_file <- read_excel("C:/Users/Dru/Desktop/Cartama_paper/files/Lenticel_Damage_Summary_All_Harvest.xlsx")
 glimpse(Lenticel_file)
@@
  plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure1.png",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
 
@@
  plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure2.png",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
 

### 2022-03-09 R/Paper_plots_microbial_ecology.Rmd
figures check

@@
 ```
-*Supplementary figure 3.* Lenticel damage for avocado cv.
+*Supplementary figure 1.* Lenticel damage for avocado cv.
 Hass fruits used for the microbial-community analysis.
@@
  plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Supplementary figure 1.png",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
 ```
@@
 Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida and El Sinai farms during the traviesa harvest of 2020.
-Shown are the means and standard deviations for the alfa diversity index richness (A), Shannon (B), and Faith (C) alpha-diversity and the asterisk denote statistic differences at the 99.0% () and 99.9% () confidence level according to the t test (n: 6).
+Bars and error bars represent mean and standard deviation for the alfa diversity index richness (A), Shannon (B), and Faith pd (C) alpha-diversity (n: 6).
+The points show the alfa diversity metrics the fruits and the asterisk denote statistic differences at the 95.0 % confidence level (*) according to the t test.
 
@@
  alpha_plot<-grid.arrange(r + labs(tag = 'A'),s + labs(tag = 'B'), f + labs(tag = 'C'), ncol=3,nrow=1)
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure 3.png",plot=alpha_plot,dpi = 300,width = 9,height = 4,units = c("in"))
 ```
@@
         panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=11,family = "serif"), plot.margin = margin(1, 0.6, 1, 1, "cm"))  +
-  scale_colour_manual(values=c("gray85","gray65","gray85","gray65"),labels = c("Escondida_Mild","Escondida_Severe", "Sinai_Mild","Sinai_Severe"))+  
+  scale_colour_manual(values=c("gray85","gray55","gray85","gray55"),labels = c("Escondida_Mild","Escondida_Severe", "Sinai_Mild","Sinai_Severe"))+  
   stat_ellipse(type = "t", size=0.5) + theme(legend.position = "bottom") +
-  labs(x = "PCoA (60.4%)", y= "PCoA (12.2%)")
+  labs(x = "PCoA (60.4%)", y= "PCoA (12.2%)")+ guides(colour = guide_legend(order = 2), 
+              shape = guide_legend(order = 1))
 legend <- get_legend(PCoA)
@@
         panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=11,family = "serif"), plot.margin = margin(0.71, 1, 1, 0.6, "cm"))  +
-  scale_colour_manual(values=c("gray85","gray65","gray85","gray65"),labels =
+  scale_colour_manual(values=c("gray85","gray55","gray85","gray55"),labels =
                         c("Escondida_Mild","Escondida_Severe",
@@
              widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure 4.png",plot=po,dpi = 300,width = 9,height = 6,units = c("in"))
 ```
@@
         panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  theme(legend.title = element_blank(),legend.text = element_text(family="serif",size=10)) + 
+  theme(legend.title = element_blank(),legend.text = element_text(family="serif",size=10)) + theme(legend.position="bottom")+
   theme(strip.text.x = element_text(size = 12 , family = 'serif'))
@@
 
+*Fig 5.* Taxonomic composition of the fungal communities of the avocado cv.
+Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida and El Sinai during the traviesa harvest of 2020.
+Shown are the relative abundances of the fungal families of the entire communities (A) and the genus for the communities of Ascomycota (B) and Basidiomycota (C).
+
 ```{r}
@@
 
-po<-grid.arrange(p1+labs(tag= "A"),p3+labs(tag = "B"),p2+labs(tag = "C"), ncol=1,nrow = 3)
+#po<-grid.arrange(p1+labs(tag= "A"),p3+labs(tag = "B"),p2+labs(tag = "C"), ncol=1,nrow = 3)
 
-p2/p3 
+po<-ggarrange(p1+labs(tag= "A"),                                                
+          ggarrange(p2+labs(tag= "B"), p3+labs(tag= "C"), nrow = 2), 
+          ncol = 2    , widths = c(0.71,1)                              
+) 
+po
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure 5.png",plot=po,dpi = 300,width = 10,height = 7,units = c("in"))
+#p2/p3 
 ```
+
+### diferential abundance analysis
+
+loading the data for diferencial abundance annalysis-Escondida
+
+```{r escondida diferential abundance}
+
+biomfile <- import_biom(paste(path,"/ASVs_enrich_Escondida.biom",sep=""))
+biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real1.txt",sep=""))
+biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
+colnames(tax_table(biomfile_merged)) <- c( "Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
+sam <-sample_data(biomfile_merged)
+otu.table <- otu_table(biomfile_merged)
+otu.table<-otu.table[!(otu.table[,1]<0.0005&otu.table[,2]<0.0005),]
+taxa <- tax_table(biomfile_merged)
+tree <- read_tree(paste(path,"/tree.nwk",sep = ""))
+otutax = phyloseq(otu.table, taxa)
+merge2 = merge_phyloseq(otutax, sam, tree)
+GP.chl <- merge2
+y<-as.data.frame(otu_table(GP.chl))
+y <- y %>%   rownames_to_column(var = "ASVs")
+
+mi_df <- data.frame(
+  "ASVs" = c(y$ASVs,y$ASVs), 
+  "Abundance" = c(y$Escondida_Severo,y$Escondida_Leve), 
+  "Farm" = c(rep("Escondida_Severe", length(y$Escondida_Severo)),rep("Escondida_Mild", length(y$Escondida_Leve)))
+)
+mi_df$ASVs <- factor(mi_df$ASVs,c(phy_tree(GP.chl)$tip.label))
+
+head(mi_df)
+
+```
+
+## Escondida plot
+
+*Fig 6.* Taxonomy and relative abundance of the amplicon sequence variants (ASVs) enriched (p-value < 0.05) in the fungal communities of avocado cv.
+Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida during the traviesa harvest of 2020.
+Shown are the taxonomic relation (A) and the relative abundances (B) of the ASVs group by color according to the clade (Supplementary Table 5).
+```{r escondida dif abundance plot}
+p<-plot_tree(GP.chl,text.size=5,method = "treeonly",nodelabf=nodeplotboot(size = 5))+
+  theme(panel.grid.major = element_blank(),
+        plot.margin= margin(t =-0.02, r = 0, b = 1.55, l = 0, unit = "cm"),
+        panel.grid.minor = element_blank())+  geom_text(x=0.05, y=43,label="A",size=5)
+
+p1<-ggplot(mi_df, aes(x=ASVs, y =Abundance*100, fill=Farm ))+  scale_fill_manual(values=c("Escondida_Leve" = "gray85", "Escondida_Severo" = "gray50"),labels = c("Mild", "Severe"))+ theme_classic()+scale_y_continuous(expand = c(0, 0))+
+  theme(panel.grid.major = element_blank(),
+        plot.margin= margin(t = 0.9, r = 0, b = 0.5, l = -0.50, unit = "cm"),
+        axis.ticks.x  = element_line(colour = "black"),axis.ticks.y  = element_line(colour = "white"),
+        axis.title.x = element_text(face="plain",family = "serif", colour="black", size=22),
+        axis.ticks.length.y = unit(0.05, "cm"),axis.ticks.length.x = unit(0.2, "cm"),
+        axis.text.x  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=20),
+        axis.text.y  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=17,margin = margin(t = 0.05, unit = "cm")),
+        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
+        panel.border = element_blank(), legend.title = element_text(size=24,family = "serif"), legend.text=element_text(size=20,family = "serif"))+
+  geom_bar(stat="identity")+ coord_flip() +
+
+   annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "yellow") +
+   annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
+   annotate("text", x = 3.8, y = 30, label = "Not_clasified", parse = TRUE,size=9,family = "serif", hjust = 1)+
+  annotate("rect", xmin = 4.5, xmax = 5.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "darkseagreen")+
+   annotate("rect", xmin = 5.5, xmax = 15.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "black") +
+   annotate("rect", xmin = 15.5, xmax = 19.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "cyan4")+
+   annotate("rect", xmin = 4.5, xmax = 19.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
+   annotate("text", x = 18.8, y = 30, label = "Basidiomycetes", parse = TRUE,size=9,family = "serif", hjust = 1)+
+   annotate("rect", xmin = 19.5, xmax = 20.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "palegreen4") +
+   annotate("rect", xmin = 20.5, xmax = 24.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "red4") +
+   annotate("rect", xmin = 24.5, xmax = 25.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "yellow4") +
+  annotate("rect", xmin = 25.5, xmax = 37.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "cyan4") +
+   annotate("rect", xmin = 37.5, xmax = 41.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "darkseagreen") +
+   annotate("rect", xmin = 41.5, xmax = 43.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "black") +
+   annotate("rect", xmin = 19.5, xmax = 43.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
+   annotate("text", x = 42.8, y = 30, label = "Ascomycetes", parse = TRUE,size=9,family = "serif", hjust = 1)+  
+   annotate("text", x = 43, y = 33.5, label = "I", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 41, y = 33.5, label = "II", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 37, y = 33.5, label = "III", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 25, y = 33.5, label = "IV", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 24, y = 33.5, label = "V", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 20, y = 33.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 19, y = 33.5, label = "VII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 15, y = 33.5, label = "VIII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 5, y = 33.5, label = "IX", parse = TRUE,size=6,family = "serif", hjust = 1)+
+  annotate("text", x = 4, y = 33.5, label = "X", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+labs( y= "Relative abundance (%)", x="")+ labs(fill = "Lenticel damage")
+
+po<-ggarrange(p,p1+labs(tag= "B"),   ncol = 2    , widths = c(0.5,1)) 
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Fig 6.png",dpi = 300,width = 13.5, height = 12, units = c("in"))
+```
+
+loading the data for diferencial abundance annalysis-Sinai
+
+```{r Sinai diferential abundance}
+
+biomfile <- import_biom(paste(path,"/ASVs_enrich_Sinai.biom",sep=""))
+biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real1.txt",sep=""))
+biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
+colnames(tax_table(biomfile_merged)) <- c( "Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
+sam <-sample_data(biomfile_merged)
+otu.table <- otu_table(biomfile_merged)
+head(otu.table)
+otu.table<-otu.table[!(otu.table[,1]<0.0005&otu.table[,2]<0.0005),]
+taxa <- tax_table(biomfile_merged)
+tree <- read_tree(paste(path,"/tree.nwk",sep = ""))
+otutax = phyloseq(otu.table, taxa)
+merge2 = merge_phyloseq(otutax, sam, tree)
+GP.chl <- merge2
+y<-as.data.frame(otu_table(GP.chl))
+y <- y %>%   rownames_to_column(var = "ASVs")
+
+mi_df <- data.frame(
+  "ASVs" = c(y$ASVs,y$ASVs), 
+  "Abundance" = c(y$Sinai_Severo,y$Sinai_Leve), 
+  "Farm" = c(rep("Sinai_Severe", length(y$Sinai_Severo)),rep("Sinai_Mild", length(y$Sinai_Leve)))
+)
+mi_df$ASVs <- factor(mi_df$ASVs,c(phy_tree(GP.chl)$tip.label))
+
+mi_df
+```
+*Fig 7.* Taxonomy and relative abundance of the amplicon sequence variants (ASVs) enriched (p- value < 0.05) in the fungal communities of avocado cv.
+Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Sinai during the traviesa harvest of 2020.
+Shown are the taxonomic relation (A) and the relative abundances (B) of the ASVs group by color according to the clade (Supplementary Table 6).
+```{r sinai plot}
+p<-plot_tree(GP.chl,text.size=15,method = "treeonly",nodelabf=nodeplotboot(size = 4))+
+       theme(panel.grid.major = element_blank(),
+             plot.margin= margin(t =-0.1, r = 0, b = 1.3, l = 0, unit = "cm"),
+             panel.grid.minor = element_blank()) +  geom_text(x=0.05, y=78,label="A",size=5)
+
+p1<-ggplot(mi_df, aes(x=ASVs, y =Abundance*100, fill=Farm ))+  scale_fill_manual(values=c("Sinai_Leve" = "gray85", "Sinai_Severo" = "gray50"),labels =c("Mild", "Severe"))+ theme_classic()+scale_y_continuous(expand = c(0, 0))+
+  theme(panel.grid.major = element_blank(),
+        plot.margin= margin(t = 0.9, r = 0, b = 0.5, l = -0.50, unit = "cm"),
+        axis.ticks.x  = element_line(colour = "black"),axis.ticks.y  = element_line(colour = "white"),
+        axis.title.x = element_text(face="plain",family = "serif", colour="black", size=22),
+        axis.ticks.length.y = unit(0.05, "cm"),axis.ticks.length.x = unit(0.2, "cm"),
+        axis.text.x  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=20),
+        axis.text.y  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=13,margin = margin(t = 0.05, unit = "cm")),
+        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
+        panel.border = element_blank(), legend.title = element_text(size=24,family = "serif"), legend.text=element_text(size=20,family = "serif"))+
+  geom_bar(stat="identity")+ coord_flip() +
+
+        annotate("rect", xmin = 0, xmax = 3.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "yellow") +
+        annotate("rect", xmin = 0, xmax = 3.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
+        annotate("text", x = 2.2, y = 20, label = "Not_clasified", parse = TRUE,size=7,family = "serif", hjust = 1)+
+
+         annotate("rect", xmin = 3.5, xmax = 27.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "black") +
+        annotate("rect", xmin = 27.5, xmax = 29.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "red4") +
+        annotate("rect", xmin = 29.5, xmax = 33.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "cyan4")+
+        annotate("rect", xmin = 3.5, xmax = 33.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
+        annotate("text", x = 29.2, y = 20, label = "Basidiomycetes", parse = TRUE,size=7,family = "serif", hjust = 1)+
+    annotate("rect", xmin = 33.5, xmax = 37.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "palegreen4") +
+    annotate("rect", xmin = 37.5, xmax = 42.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "red4") +
+    annotate("rect", xmin = 42.5, xmax = 49.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "yellow4") +
+    annotate("rect", xmin = 49.5, xmax = 70.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "cyan4") +
+    annotate("rect", xmin = 70.5, xmax = 76.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "darkseagreen") +
+    annotate("rect", xmin = 76.5, xmax = 78.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "black") +
+    annotate("rect", xmin = 33.5, xmax = 78.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
+    annotate("text", x = 77.2, y = 20, label = "Ascomycetes", parse = TRUE,size=7,family = "serif", hjust = 1)+
+
+   annotate("text", x = 77.5, y = 23.5, label = "I", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 75, y = 23.5, label = "II", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 69, y = 23.5, label = "III", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 48, y = 23.5, label = "IV", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 41, y = 23.5, label = "V", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 36, y = 23.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+  
+   annotate("text", x = 30, y = 23.5, label = "VII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+    annotate("text", x = 28.5, y = 23.5, label = "VIII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+    annotate("text", x = 27, y = 23.5, label = "IX", parse = TRUE,size=6,family = "serif", hjust = 1)+
+    annotate("text", x = 2, y = 23.5, label = "X", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+  labs( y= "Relative abundance (%)", x="")+ labs(fill = "Lenticel damage")
+
+po<-ggarrange(p,p1+labs(tag= "B"),   ncol = 2    , widths = c(0.5,1)) 
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Fig7.png",plot=po,dpi = 300,width = 13.5,height = 12,units = c("in"))
+```

### 2022-03-19 R/Paper_plots_microbial_ecology.Rmd
v2.2

@@
 otu.table <- otu_table(biomfile_merged)
-otu.table<-otu.table[!(otu.table[,1]<0.0005&otu.table[,2]<0.0005),]
+#otu.table<-otu.table[!(otu.table[,1]<0.0005&otu.table[,2]<0.0005),]
+otu.table<-otu.table[!(otu.table[,1]<0.002&otu.table[,2]<0.002),]
 taxa <- tax_table(biomfile_merged)
@@
 
-head(mi_df)
+print(mi_df)
 
@@
         plot.margin= margin(t =-0.02, r = 0, b = 1.55, l = 0, unit = "cm"),
-        panel.grid.minor = element_blank())+  geom_text(x=0.05, y=43,label="A",size=5)
+        panel.grid.minor = element_blank())+  geom_text(x=0.05, y=29.95,label="A",size=5)
 
-p1<-ggplot(mi_df, aes(x=ASVs, y =Abundance*100, fill=Farm ))+  scale_fill_manual(values=c("Escondida_Leve" = "gray85", "Escondida_Severo" = "gray50"),labels = c("Mild", "Severe"))+ theme_classic()+scale_y_continuous(expand = c(0, 0))+
+p1<-ggplot(mi_df, aes(x=ASVs, y =Abundance*100, fill=Farm ))+  
+  scale_fill_manual(values=c("Escondida_Mild" = "gray85", "Escondida_Severe" = "gray40"),labels = c("Mild", "Severe"))+
+  theme_classic()+scale_y_continuous(expand = c(0, 0))+
   theme(panel.grid.major = element_blank(),
@@
   geom_bar(stat="identity")+ coord_flip() + 
+  annotate("rect", xmin = 0, xmax = 3.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "yellow") +
+   annotate("rect", xmin = 0, xmax = 3.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
+   annotate("text", x = 2.7, y = 30, label = "Not_clasified", parse = TRUE,size=9,family = "serif", hjust = 1)+
 
-   annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "yellow") +
-   annotate("rect", xmin = 0, xmax = 4.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
-   annotate("text", x = 3.8, y = 30, label = "Not_clasified", parse = TRUE,size=9,family = "serif", hjust = 1)+
-  annotate("rect", xmin = 4.5, xmax = 5.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "darkseagreen")+
-   annotate("rect", xmin = 5.5, xmax = 15.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "black") +
-   annotate("rect", xmin = 15.5, xmax = 19.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "cyan4")+
-   annotate("rect", xmin = 4.5, xmax = 19.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
-   annotate("text", x = 18.8, y = 30, label = "Basidiomycetes", parse = TRUE,size=9,family = "serif", hjust = 1)+
-   annotate("rect", xmin = 19.5, xmax = 20.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "palegreen4") +
-   annotate("rect", xmin = 20.5, xmax = 24.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "red4") +
-   annotate("rect", xmin = 24.5, xmax = 25.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "yellow4") +
-  annotate("rect", xmin = 25.5, xmax = 37.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "cyan4") +
-   annotate("rect", xmin = 37.5, xmax = 41.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "darkseagreen") +
-   annotate("rect", xmin = 41.5, xmax = 43.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "black") +
-   annotate("rect", xmin = 19.5, xmax = 43.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
-   annotate("text", x = 42.8, y = 30, label = "Ascomycetes", parse = TRUE,size=9,family = "serif", hjust = 1)+  
-   annotate("text", x = 43, y = 33.5, label = "I", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 41, y = 33.5, label = "II", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 37, y = 33.5, label = "III", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 25, y = 33.5, label = "IV", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 24, y = 33.5, label = "V", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 20, y = 33.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 19, y = 33.5, label = "VII", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 15, y = 33.5, label = "VIII", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 5, y = 33.5, label = "IX", parse = TRUE,size=6,family = "serif", hjust = 1)+
-  annotate("text", x = 4, y = 33.5, label = "X", parse = TRUE,size=6,family = "serif", hjust = 1)+
+  annotate("text", x = 3, y = 33.5, label = "IX", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+  annotate("rect", xmin = 3.5, xmax = 4.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "darkseagreen")+
+   annotate("rect", xmin = 4.5, xmax = 10.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "black") +
+
+   annotate("rect", xmin = 10.5, xmax = 13.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "cyan4")+
+
+   annotate("rect", xmin = 3.5, xmax = 13.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
+   annotate("text", x = 12.8, y = 30, label = "Basidiomycetes", parse = TRUE,size=9,family = "serif", hjust = 1)+
+     annotate("text", x = 13, y = 33.5, label = "VIII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 9.8, y = 33.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("text", x = 4, y = 33.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("rect", xmin = 13.5, xmax = 14.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "palegreen4") +
+   annotate("text", x = 14, y = 33.5, label = "V", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("rect", xmin = 14.5, xmax = 17.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "red4") +
+
+  annotate("text", x = 17, y = 33.5, label = "IV", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("rect", xmin = 17.5, xmax = 27.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "yellow4") +
+     annotate("text", x = 27, y = 33.5, label = "III", parse = TRUE,size=6,family = "serif", hjust = 1)+
+  annotate("rect", xmin = 27.5, xmax = 28.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "cyan4") +
+  annotate("text", x = 28, y = 33.5, label = "II", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("rect", xmin = 28.5, xmax = 30.5, ymin = 0, ymax = 35,   alpha = .1,  fill = "darkseagreen") +
+     annotate("text", x = 30, y = 33.5, label = "I", parse = TRUE,size=6,family = "serif", hjust = 1)+
+   annotate("rect", xmin = 13.5, xmax = 30.5, ymin = 0, ymax = 35,   alpha = .1,  col = "black") +
+   annotate("text", x = 29.8, y = 30, label = "Ascomycetes", parse = TRUE,size=9,family = "serif", hjust = 1)+
 
@@
 head(otu.table)
-otu.table<-otu.table[!(otu.table[,1]<0.0005&otu.table[,2]<0.0005),]
+otu.table<-otu.table[!(otu.table[,1]<0.002&otu.table[,2]<0.002),]
 taxa <- tax_table(biomfile_merged)
@@
              plot.margin= margin(t =-0.1, r = 0, b = 1.3, l = 0, unit = "cm"),
-             panel.grid.minor = element_blank()) +  geom_text(x=0.05, y=78,label="A",size=5)
+             panel.grid.minor = element_blank()) +  geom_text(x=0.05, y=38,label="A",size=5)
 
-p1<-ggplot(mi_df, aes(x=ASVs, y =Abundance*100, fill=Farm ))+  scale_fill_manual(values=c("Sinai_Leve" = "gray85", "Sinai_Severo" = "gray50"),labels =c("Mild", "Severe"))+ theme_classic()+scale_y_continuous(expand = c(0, 0))+
+p1<-ggplot(mi_df, aes(x=ASVs, y =Abundance*100, fill=Farm ))+  scale_fill_manual(values=c("Sinai_Mild" = "gray85", "Sinai_Severe" = "gray50"),labels =c("Mild", "Severe"))+ theme_classic()+scale_y_continuous(expand = c(0, 0))+
   theme(panel.grid.major = element_blank(),
@@
 
-        annotate("rect", xmin = 0, xmax = 3.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "yellow") +
-        annotate("rect", xmin = 0, xmax = 3.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
-        annotate("text", x = 2.2, y = 20, label = "Not_clasified", parse = TRUE,size=7,family = "serif", hjust = 1)+
+        annotate("rect", xmin = 0, xmax = 2.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "yellow") +
+        annotate("rect", xmin = 0, xmax = 2.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
+        annotate("text", x = 1.2, y = 20, label = "Not_clasified", parse = TRUE,size=7,family = "serif", hjust = 1)+
+  annotate("text", x = 1.7, y = 23.5, label = "IX", parse = TRUE,size=6,family = "serif", hjust = 1)+
 
-         annotate("rect", xmin = 3.5, xmax = 27.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "black") +
-        annotate("rect", xmin = 27.5, xmax = 29.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "red4") +
-        annotate("rect", xmin = 29.5, xmax = 33.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "cyan4")+
-        annotate("rect", xmin = 3.5, xmax = 33.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
-        annotate("text", x = 29.2, y = 20, label = "Basidiomycetes", parse = TRUE,size=7,family = "serif", hjust = 1)+
-    annotate("rect", xmin = 33.5, xmax = 37.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "palegreen4") +
-    annotate("rect", xmin = 37.5, xmax = 42.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "red4") +
-    annotate("rect", xmin = 42.5, xmax = 49.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "yellow4") +
-    annotate("rect", xmin = 49.5, xmax = 70.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "cyan4") +
-    annotate("rect", xmin = 70.5, xmax = 76.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "darkseagreen") +
-    annotate("rect", xmin = 76.5, xmax = 78.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "black") +
-    annotate("rect", xmin = 33.5, xmax = 78.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
-    annotate("text", x = 77.2, y = 20, label = "Ascomycetes", parse = TRUE,size=7,family = "serif", hjust = 1)+
+         annotate("rect", xmin = 2.5, xmax = 13.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "black") +
+        annotate("rect", xmin = 13.5, xmax = 14.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "red4") +
+      annotate("rect", xmin = 2.5, xmax = 14.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
+        annotate("text", x = 13.8, y = 20, label = "Basidiomycetes", parse = TRUE,size=7,family = "serif", hjust = 1)+
 
-   annotate("text", x = 77.5, y = 23.5, label = "I", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 75, y = 23.5, label = "II", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 69, y = 23.5, label = "III", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 48, y = 23.5, label = "IV", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 41, y = 23.5, label = "V", parse = TRUE,size=6,family = "serif", hjust = 1)+
-   annotate("text", x = 36, y = 23.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+  
-   annotate("text", x = 30, y = 23.5, label = "VII", parse = TRUE,size=6,family = "serif", hjust = 1)+
-    annotate("text", x = 28.5, y = 23.5, label = "VIII", parse = TRUE,size=6,family = "serif", hjust = 1)+
-    annotate("text", x = 27, y = 23.5, label = "IX", parse = TRUE,size=6,family = "serif", hjust = 1)+
-    annotate("text", x = 2, y = 23.5, label = "X", parse = TRUE,size=6,family = "serif", hjust = 1)+
+ annotate("text", x = 14, y = 23.5, label = "VII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+    annotate("text", x = 13, y = 23.5, label = "VIII", parse = TRUE,size=6,family = "serif", hjust = 1)+
+          annotate("rect", xmin = 14.5, xmax = 16.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "cyan4")+
+
+   annotate("text", x = 19, y = 23.5, label = "V", parse = TRUE,size=6,family = "serif", hjust = 1)+  
+   annotate("rect", xmin = 16.5, xmax = 19.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "palegreen4") +
+   annotate("text", x = 16, y = 23.5, label = "VI", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+    annotate("rect", xmin = 19.5, xmax = 22.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "red4") +
+
+   annotate("text", x = 22, y = 23.5, label = "IV", parse = TRUE,size=6,family = "serif", hjust = 1)+
+    annotate("rect", xmin = 22.5, xmax = 31.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "yellow4") +
+
+   annotate("text", x = 31, y = 23.5, label = "III", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+    annotate("rect", xmin = 31.5, xmax = 37.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "cyan4") +
+
+   annotate("text", x = 37, y = 23.5, label = "II", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+    annotate("rect", xmin = 37.5, xmax = 38.5, ymin = 0, ymax = 25,   alpha = .1,  fill = "darkseagreen") +
+
+   annotate("text", x = 38, y = 23.5, label = "I", parse = TRUE,size=6,family = "serif", hjust = 1)+
+
+    annotate("rect", xmin = 14.5, xmax = 38.5, ymin = 0, ymax = 25,   alpha = .1,  col = "black") +
+    annotate("text", x = 37.8, y = 20, label = "Ascomycetes", parse = TRUE,size=7,family = "serif", hjust = 1)+
 

### 2023-04-01 R/Paper_plots_lenticel_damage.Rmd
before last revision

@@
 loadfonts(device = "win")
+library(ggsignif)
+library(ggpubr)
 
@@
 colnames(df)[which(names(df) == "Incidencia_1")] <- "Inc_21dph"
+df$Inc_increase <- df$Inc_21dph-df$Inc_0dph
+df$Sev_increase <- df$Sev_21dph-df$Sev_0dph
+
 glimpse(df)
@@
   }
-mat <- data.frame(rep(c("2019_m" , "2020_m" , "2020_t" , "2021_t") , 13) , c(rep("Escondida" , 24) , rep("Sinai" , 28)) , sev , inc)
+mat <- data.frame(rep(c("2019_m" , "2020_m" , "2020_t" , "2021_t") , 13) , c(rep("Escondida" , 20) , rep("Sinai" , 32)) , sev , inc)
 
@@
 p <- p + theme(strip.text.x = element_text(size = 14,family = 'serif'))
+p
 
@@
 p1 <- p1 + geom_jitter()+ facet_wrap(~Farm) + theme_classic() 
-p1 <- p1 +  xlab("") + ylab("Necrotic spots")
+p1 <- p1 +  xlab("") + ylab("Number of necrotic spots")
 p1 <- p1 + theme(axis.title =element_text(size = 14 , family = 'serif'))
@@
 p1 <- p1 + theme(strip.text.x = element_text(size = 14 , family = 'serif'))
+p1
 
@@
  plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
-ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure1.png",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure1_new.jpg",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
 
@@
 inc <- c(df1$Inc_0dph , df1$Inc_21dph)
+
+###stack plot
+#sev <- c(df1$Sev_0dph , df1$Sev_increase)
+#inc <- c(df1$Inc_0dph , df1$Inc_increase)
 farm <- c(df1$Farm , df1$Farm)
@@
 p <-  ggplot(mat1, aes(x = factor(Time), y = Severity)) + 
-      geom_bar(stat="summary", color="black", positio=position_dodge(), fill= rep(c("gray95","gray85") ,2), fun = mean) +
+      geom_bar(stat="summary", color="black", positio=position_dodge(), fill= rep(c("gray99","gray95") ,2), fun = mean) +
       stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
@@
 p <- p + theme(strip.text.x = element_text(size = 14,family = 'serif'))
-p <- p + scale_color_manual(name = "Harvest", values =  rep(c("gray70","gray40") ,2))
+p <- p + scale_color_manual(name = "Harvest",  values =  c("gray88","gray70","gray47","gray0"))
 p <- p + theme(legend.text = element_text(size=12, angle=0,family = 'serif'),
                 legend.title = element_text(face="bold",size=12, angle=0,family = 'serif'))
+p
 
@@
 p1 <-  ggplot(mat1, aes(x = factor(Time), y = Incidence)) + 
-      geom_bar(stat="summary", color="black", positio=position_dodge(), fill= rep(c("gray95","gray85") ,2), fun = mean) +
+      geom_bar(stat="summary", color="black", positio=position_dodge(), fill= rep(c("gray99","gray95") ,2), fun = mean) +
       stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar", color="black", width=0.2) 
@@
 p1 <- p1 + facet_wrap(~ Farm) + theme_classic() 
-p1 <- p1 +  xlab("") + ylab("Necrotic spots")
+p1 <- p1 +  xlab("") + ylab("Number of necrotic spots")
 p1 <- p1 + theme(axis.title =element_text(size=14,family = 'serif'))
@@
 p1 <- p1 + theme(strip.text.x = element_text(size = 14,family = 'serif'))
-p1 <- p1 + scale_color_manual(name = "Harvest", values =  rep(c("gray70","gray40") ,2))
+p1 <- p1 + scale_color_manual(name = "Harvest", values =  c("gray88","gray70","gray47","gray0"))
 p1 <- p1 + theme(legend.text = element_text(size=12, angle=0,family = 'serif'),
@@
  plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
-ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure2.png",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure2_new.jpg",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
 
 ```
+```{r df_for_barplot plots}
+
+df1 <- na.omit(df)
+
+sev <- c(df1$Sev_0dph , df1$Sev_21dph)
+inc <- c(df1$Inc_0dph , df1$Inc_21dph)
+
+farm <- c(df1$Farm , df1$Farm)
+time <-factor(c(rep("0dph",length(sev)/2) , rep("21dph",length(sev)/2)))
+harvest <- c(df1$Harvest , df1$Harvest)
+
+mat <- data.frame(Farm = farm, Time = time , Harvest = harvest, Severity = sev , Incidence = inc)
+
+mat_mean<-tapply(mat$Severity , list(mat$Time,mat$Harvest,mat$Farm),mean)
+mat_mean1<-tapply(mat$Incidence , list(mat$Time,mat$Harvest,mat$Farm),mean)
+mat_se<-tapply(mat$Severity , list(mat$Time,mat$Harvest,mat$Farm),sd)/sqrt(table(mat$Time,mat$Harvest,mat$Farm))
+mat_se1<-tapply(mat$Incidence , list(mat$Time,mat$Harvest,mat$Farm),sd)/sqrt(table(mat$Time,mat$Harvest,mat$Farm))
+n <- table(mat$Time,mat$Harvest,mat$Farm)
+
+mat1<-data.frame(Farm = c(rep("Escondida" , 8) , rep("Sinai" , 8)), Time = rep(c(rep("0dph",4) , rep("21dph",4)) , 2) ,
+                 Harvest = rep(c("2019_m" , "2020_m" , "2020_t" , "2021_t") , 4), 
+                 Severity = c(mat_mean[1,,1] , mat_mean[2,,1] , mat_mean[1,,2] , mat_mean[2,,2]),
+                 Severity_se = c(mat_se[1,,1] , mat_se[2,,1] , mat_se[1,,2] , mat_se[2,,2]),
+                 Incidence = c(mat_mean1[1,,1] , mat_mean1[2,,1] , mat_mean1[1,,2] , mat_mean1[2,,2]),
+                 Incidence_se = c(mat_se1[1,,1] , mat_se1[2,,1] , mat_se1[1,,2] , mat_se1[2,,2]))
+
+head(mat1)
+
+```
+* The barplot showing the increase in the severity of lenticel damage during the cold storage.
+The bars and error bars represent the severity mean and standard deviation observed in the farms at the two evaluations (0 dph and 21 dph), and the points represent the severity mean for the harvest in the farm.
+
+```{r severity in time}
+
+data_hline <- data.frame(Farm = c(rep("Escondida",4),rep( "Sinai",4)),
+                         x = c(0.7,1.7,2.7,3.7,0.7,1.7,2.7,3.7), y = c(1.2, 2.4,0.9,4.7,2.8,4.6,5.4,3.6),xend = c(1.3,2.3,3.3,4.3,1.3,2.3,3.3,4.3), yend = c(1.2, 2.4,0.9,4.7,2.8,4.6,5.4,3.6), label = rep("*",8))
+
+p <-  ggplot(mat1, aes(x = factor(Harvest, levels = c("2019_m" , "2020_t" , "2020_m" , "2021_t")), y = Severity, fill = factor(Time))) + geom_bar(stat="identity", positio=position_dodge())     
+p <- p + scale_fill_manual(values=c("gray90", "gray80"))
+p <- p + geom_errorbar(aes(ymin=Severity-Severity_se, ymax=Severity+Severity_se), width=.2,position=position_dodge(.9)) 
+p <- p + facet_grid(~ Farm) + theme_classic() 
+p <- p +  xlab("") + ylab("Necrotic Area (%)") + labs(fill='Days postharvest') 
+p <- p + theme(axis.title =element_text(size=14,family = 'serif'))
+p <- p +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
+              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
+p <- p + theme(strip.text.x = element_text(size = 14,family = 'serif'))
+p <- p + theme(legend.text = element_text(size=12, angle=0,family = 'serif'),
+                legend.title = element_text(face="bold",size=12, angle=0,family = 'serif'))
+
+p <- p + geom_segment(data = data_hline,aes(x = x,y = y,xend = xend, yend = yend),inherit.aes = FALSE) 
+p <- p +geom_text(data = data_hline,aes(label = label,x = x+0.3,y = y+0.2),inherit.aes = FALSE)
+
+```
+* The barplot showing the increase in the Incidence of lenticel damage during the cold storage.
+The bars and error bars represent the incidence mean and standard deviation observed in the farms at the two evaluations (0 dph and 21 dph), and the points represent the severity mean for the harvest in the farm.
+
+```{r incidence in time}
+
+p1 <-  ggplot(mat1, aes(x = factor(Harvest, levels = c("2019_m" , "2020_t" , "2020_m" , "2021_t")), y = Incidence, fill = factor(Time))) + geom_bar(stat="identity", positio=position_dodge())     
+p1 <- p1 + scale_fill_manual(values=c("gray90", "gray80"))
+p1 <- p1 + geom_errorbar(aes(ymin=Incidence-Incidence_se, ymax=Incidence+Incidence_se), width=.2,position=position_dodge(.9)) 
+p1 <- p1 + facet_wrap(~ Farm) + theme_classic() 
+p1 <- p1 +  xlab("Harvest") + ylab("Number of necrotic spots") + labs(fill='Days postharvest') 
+p1 <- p1 + theme(axis.title =element_text(size=14,family = 'serif'))
+p1 <- p1 +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,family = 'serif'),
+              axis.text.y = element_text(face="bold",size=12, angle=0,family = 'serif'))
+p1 <- p1 + theme(strip.text.x = element_text(size = 14,family = 'serif'))
+p1 <- p1 + scale_color_manual(name = "Harvest", values =  c("gray88","gray70","gray47","gray0"))
+p1 <- p1 + theme(legend.text = element_text(size=12, angle=0,family = 'serif'),
+                legend.title = element_text(face="bold",size=12, angle=0,family = 'serif'))
+
+data_hline <- data.frame(Farm = c(rep("Escondida",4),rep( "Sinai",4)),
+                         x = c(0.7,1.7,2.7,3.7,0.7,1.7,2.7,3.7), y = c(88, 165,70,203,238,217,256,187),xend = c(1.3,2.3,3.3,4.3,1.3,2.3,3.3,4.3), yend = c(88, 165,70,203,238,217,256,187), label = rep("*",8))
+
+p1 <- p1 + geom_segment(data = data_hline,aes(x = x,y = y,xend = xend, yend = yend),inherit.aes = FALSE) 
+p1 <- p1 + geom_text(data = data_hline,aes(label = label,x = x+0.3,y = y+5),inherit.aes = FALSE)
+p1
+
+```
+*Fig 2.* Lenticel damage for avocado cv.
+Hass fruits collected from the La Escondida and El Sinai farms between 2019 and 2021 at harvest time (0 days post-harvest, 0 dph) and after 21 days of storage at 6C (21 days post-harvest, 21 dph).
+Shown are the means and standard errors for the severity (A) and incidence (B) of the damage for the two evaluatin points (0 dph and 21 dph).
+The * denotes statistical differences at a 95% confidence level according to the  generalized linear mixed models, and the letter after the year denotes main (m) and traviesa (t) harvest.
+
+```{r severity and incidence in time plot}
+
+ plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure1_new.jpg",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
+
+```

### 2023-04-01 R/Paper_plots_microbial_ecology.Rmd
before last revision

--- 2022-03-07 R/Paper_plots_microbial_ecology.Rmd
@@
 
-```{r Packages}
+```{r Packages, message=FALSE, warning=FALSE}
 
@@
 library(patchwork)
-
-path<-"C:/Users/Dru/Desktop/Cartama_paper/files/MicrobialEcology"
-
+library(car)
+library(ggimage)
+library(ggtree)
+library(TDbook)
+library(aplot)
+library(lemon)
+library(grid, lib.loc = "C:/Program Files/R/R-4.2.0/library")
+setwd("C:/Users/Dru/Desktop/Cartama_paper/microbial-ecology-avocado/Resultados_all")
 ```
@@
  plot<-grid.arrange(p + labs(tag = 'A'),p1 + labs(tag = 'B'), ncol=1,nrow=2)
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/SupplementaryFig1.jpg",plot=plot,dpi = 300,width = 7,height = 7,units = c("in"))
+```
+## Rarefraction curve plots
+
+```{r}
+
+#Curvas de rarefacci?n antes de normalizacion
+biomfile_before <- import_biom("ASVs_table6_dada2R.biom")
+biomfile_after <- import_biom("ASVs_table9_dada2R.biom")
+head(otu_table(biomfile))
+head(tax_table(biomfile))
+
+otu.table_before <- otu_table(biomfile_before)
+t.OTU.table_before <- t(otu.table_before)
+
+otu.table_after <- otu_table(biomfile_after)
+t.OTU.table_after <- t(otu.table_after)
+#head(otu_table(biomfile_before))
+#head(tax_table(biomfile))
+
+col <- c("black", "darkred", "forestgreen", "orange", "blue", "yellow", "hotpink")
+lty <- c(rep("solid",6),rep( "dashed",6), rep( "longdash", 6), rep("dotdash",6))
+#par(mar=c(5,4,2,2))
+#par(mgp=c(2.3,0.5,0))
+jpeg("rarre.jpg", units="in", width=7, height=6, res=300)
+par(mfrow=c(1,2))
+p<-rarecurve(t.OTU.table_before, col="black", step = 1000, cex = 0.8, lwd=1, label = FALSE,xlab = "Sample size", ylab = "Specie Number", ylim=c(0, 680),family="serif",cex.lab=1.4, cex.axis=1.2,lty=lty)
+
+text(-14800, 760, "A", family = "serif", xpd=NA, cex = 1.2 )
+p1<-rarecurve(t.OTU.table_after, col="black", step = 1000, cex = 0.8, lwd=1, label = FALSE,xlab = "Sample size", ylab = "Specie Number", ylim=c(0, 680),family="serif",cex.lab=1.4, cex.axis=1.2,lty=lty)
+
+text(-6000, 760, "B", family = "serif", xpd=NA, cex = 1.2 )
+dev.off()
+
+#The rarefaction curves are evaluated using the interval of step sample sizes
+#Graphical Parameters: https://www.statmethods.net/advgraphs/parameters.html
+
+```
+
+```{r severity and incidence plot}
+
+jpeg("rarre.jpg",, units="in", width=5, height=5, res=300)
+dev.off()
 ```
@@
 ```{r alfa df}
-Alfa <- read_excel(paste(path,"/Alfa.xlsx",sep=""))
+path<-"C:/Users/Dru/Desktop/Cartama_paper/microbial-ecology-avocado/Resultados_all/Alfa/"
+Alfa <- read_excel(paste(path,"Alfa.xlsx",sep=""))
 head(Alfa)
+```
+```{r alfa analisis}
+c <- subset(Alfa, Alfa$Farm == "Sinai")$Chao
+s <- subset(Alfa, Alfa$Farm == "Sinai")$Shannon_entropy
+r <- subset(Alfa, Alfa$Farm == "Sinai")$Riqueza
+f <- subset(Alfa, Alfa$Farm == "Sinai")$Faith_pd
+e <- subset(Alfa, Alfa$Farm == "Sinai")$Evenness
+
+damage <-subset(Alfa, Alfa$Farm == "Escondida")$Damage_level
+
+#names(shannon)
+#Check ANOVA assumptions
+#Homogeneity of variance
+leveneTest(c ~ damage)  #p-value > 0.05 
+#Shapiro-Wilk test
+shapiro.test(c) #p-value > 0.05 is normal
+#Independence
+durbinWatsonTest(lm(c ~ damage)) #p-value > 0.05 they are independent
+
+t.test(r~damage)
+kruskal.test(s~damage)
+summary(glm(c~damage, family = quasipoisson()))
+plot(glm(c~damage, family = poisson()))
+plot(lm(c~damage))
 ```
@@
 c <- c + theme(strip.text.x = element_text(size = 14,family = 'serif'))
-c <- c + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
+c <- c + geom_signif(test="kruskal.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
 
@@
 s <- s + theme(strip.text.x = element_text(size = 14,family = 'serif'))
-s <- s + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
+s <- s + geom_signif(test="kruskal.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
 
@@
 r <- r + theme(strip.text.x = element_text(size = 14,family = 'serif'))
-r <- r + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
+r <- r + geom_signif(test="kruskal.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
 
@@
 f <- f + theme(strip.text.x = element_text(size = 14,family = 'serif'))
-f <- f + geom_signif(test="t.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
+f <- f + geom_signif(test="kruskal.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
+
+###evenness
+e <-  ggplot(Alfa, aes(x = Damage_level, y = Evenness)) + 
+      geom_bar(stat="summary", color="black", position=position_dodge(),
+               fill=rep(c("gray90","gray70"),2),fun = mean) +
+      stat_summary(fun.data=mean_sdl, fun.args = list(mult=1), geom="errorbar",
+                   color="black", width=0.2) 
+e <- e + geom_jitter()+ facet_wrap(~Farm)+ theme_classic() 
+e <- e +  xlab("") + ylab("Evenness")+ylim(c(0, max(Alfa$Evenness)*1.1))
+e <- e + theme(axis.title =element_text(size=14,family = 'serif'))
+e <- e +  theme(axis.text.x = element_text(face="bold",size=12, angle=0,
+                                             family ='serif'),
+                  axis.text.y = element_text(face="bold",size=12, angle=0,family =
+                                               'serif'))
+e <- e + theme(strip.text.x = element_text(size = 14,family = 'serif'))
+e <- e + geom_signif(test="kruskal.test", comparisons = list(c("Mild", "Severe")), map_signif_level = T)
 
@@
 
- alpha_plot<-grid.arrange(r + labs(tag = 'A'),s + labs(tag = 'B'), f + labs(tag = 'C'), ncol=3,nrow=1)
+ alpha_plot<-grid.arrange(s + labs(tag = 'A'),c + labs(tag = 'B'), e + labs(tag = 'C'),f + labs(tag = 'D'), ncol=2,nrow=2)
+ggsave("Figure2_alfa_new.jpg",plot=alpha_plot,dpi = 300,width = 6,height = 6,units = c("in"))
 ```
@@
 ```{r uploading the CCS.biom and tree.nwk}
+
+path<-"C:/Users/Dru/Desktop/Cartama_paper/microbial-ecology-avocado/Resultados_All"
 biomfile <- import_biom(paste(path,"/css_eff.biom",sep=""))
 biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
-biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
+tree <- read_tree(paste(path,"/tree.nwk",sep=""))
+
+biomfile_mapfile_sinai<- subset(biomfile_mapfile,biomfile_mapfile$Farm1=="Sinai")
+biomfile_mapfile_escondida<-subset(biomfile_mapfile,biomfile_mapfile$Farm1=="Escondida")
+
+biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile_escondida)
 colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
 sam <-sample_data(biomfile_merged)
-
 otu.table <- otu_table(biomfile_merged)
@@
 
-tree <- read_tree(paste(path,"/tree.nwk",sep=""))
-
 otutax = phyloseq(otu.table, taxa)
 merge2 = merge_phyloseq(otutax, sam, tree)
+```
+
+###CAP
+
+```{r CAP}
+agricultural.ord<- ordinate(merge2, "CAP", "wunifrac", ~Farm*Lenticel_disease_status)
+
+agricultural_plot<- plot_ordination(merge2, agricultural.ord, type = "sites",
+                                    color = "Farm",
+                                    title = "", label = NULL)
+
+CAP = agricultural_plot  +
+  geom_point(aes(color =Farm,shape = Farm1), size = 3) +
+  theme(panel.grid.major = element_blank(), 
+        panel.grid.minor = element_blank(), 
+        rect = element_rect(fill = "white", colour = "black",size = 0.5, linetype = 1),
+        axis.ticks = element_line(colour = "black"),
+        axis.title.x = element_text(face="plain",family = "serif", colour="black", size=12),
+        axis.title.y = element_text(face="plain",family = "serif", colour="black", size=12),
+        axis.text.x  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
+        axis.text.y  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
+        panel.background = element_rect(fill = "white", colour = "black", linetype = 1, size = 0.5),
+        panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=0.1,family = "serif"), plot.margin = margin(0.755, 1, 1, 0.3, "cm"))  +
+  scale_colour_manual(values=c("gray85","gray55","gray85","gray55"),labels =
+                        c("Escondida_Mild","Escondida_Severe",
+                          "Sinai_Mild","Sinai_Severe")) + 
+  stat_ellipse(type = "t", size=0.5) + labs(x = "CAP (23.7%)", y= "CAP (45.8%)") + theme(legend.position = "right",legend.text = element_text(size=10))
+CAP
+ggsave("Figure4_new.jpg",plot=CAP,dpi = 300,width = 6,height = 5,units = c("in"))
+
+```
+
+*Fig 4* Fungal communities’ structure for fruits of avocado cv.
+Hass fruits with mild and severe lenticel damages collected from the La Escondida and El Sinai farms during the traviesa harvest of 2020.
+Cumulative sum scaling (CSS) transformed reads were used to calculate weighted unifrac distance.
+Shown is the bidimensional plane of the canonical analysis of principal coordinates (CAP) constrained by the farm and the strenght of the damage (69.5 % of the overall variance; p-value: 0.001 acording to the permanova test).
+Each point represents a fruit's fungal community, the shapes show the farm (La Escondida (circles) and El Sinai (triangles)), and the colors the damage strength (Severe (dark gray) and Mild (light gray)) of the fruit.
+The ellipses are the 95 % confidence level ellipses.
+
+```{r}
+
+#agricultural.ord<- ordinate(merge2, "CAP", "wunifrac", ~Farm1*Lenticel_damage_status)
+
+#PERMANOVA
+perm_anova.agricultural.ord1 <- anova.cca(ordinate(merge2, "CAP", "wunifrac", ~Lenticel_disease_status))
+#perm_anova.agricultural2.ord <- permutest(agricultural.ord)
+
+# P-value
+print(as.data.frame(perm_anova.agricultural.ord)["Pr(>F)"])
+```
+
+```{r PCoA and PCA plots}
+
+po<-grid.arrange(PCoA+labs(tag = "A"),CAP+  geom_text(x=-0.65, y=0.69,label="B",size=4.5, col= "black") +coord_cartesian( clip = "off"),legend, ncol=2,nrow = 2, 
+             layout_matrix = rbind(c(1,2), c(3,3)),
+             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
+ggsave("C:/Users/Dru/Desktop/Cartama_paper/Figure4.jpg",plot=po,dpi = 300,width = 7,height = 6,units = c("in"))
+```
+## Taxonomy bat plots
+Loading the ASVs table
+
+```{r data barplot}
+biomfile <- import_biom(paste(path,"/ASVs_table9_dada2R.biom",sep=""))
+##biomfile <- import_biom("ASVs_table6_dada2R.biom")
+#biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
+biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
+colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
+sample_data(biomfile_merged)
+
+plot_colors <- c( "palegoldenrod","gray90", "plum4", "lightsteelblue","darkseagreen1",
+                   "#CBD588", "#5F7FC7","#DA5724", "#8A7C64","gray30", "#508578", "#CD9BCD", "#AD6F3B",
+                  "darkseagreen4","deepskyblue1","gray50" , "yellow2", "slateblue1",
+                  "#673770","Khaki4", "#652926", "yellow3", "cadetblue3",
+                   "lightsteelblue3", "honeydew3", "gray80","thistle4","yellow4",
+                   "#5E738F", "#8A7C64","gray30", "lightpink3")
+```
+
+## Phylum barplot
+```{r}
+subset = biomfile_merged
+rel.abun = transform_sample_counts(subset, function(x) x / sum(x))
+glom <- tax_glom(rel.abun, taxrank = 'Phylum')
+data_glom<- psmelt(glom) 
+data_glom$Phylum <- as.character(data_glom$Phylum) 
+data_glom$Phylum[data_glom$Abundance < 0.03] <- "< 3% abundance"
+data_glom$Phylum[data_glom$Phylum == "unidentified"] <- "Not classified"
+data_glom$Phylum[data_glom$Phylum == "undefined"] <-"Not classified"
+data_glom$Lenticel_disease_status[data_glom$Lenticel_disease_status == "Necrotic"] <-"Severe"
+data_glom$Lenticel_disease_status[data_glom$Lenticel_disease_status == "Healthy"] <-"Mild"
+
+plot_colors <- c( "palegoldenrod","gray90", "plum4", "lightsteelblue","darkseagreen1")
+Phylum <- ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Phylum, Abundance)))+
+  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors) +
+  ylab("Relative abundance") + xlab("") +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
+        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
+        axis.line = element_line(colour = "black"),
+        axis.ticks = element_line(colour = "black"),
+        axis.title.y = element_text(face="plain", colour="black", size=13,family="serif"),
+        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=13,family="serif"),
+        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=13,family="serif"),
+        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
+        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  theme(legend.title = element_blank(),legend.text = element_text(family="serif",size=12))+
+  theme(strip.text.x = element_text(size = 13 , family = 'serif'))
+
+print(Phylum)
+
+df = data.frame(Treatment = data_glom$Farm, Phylum = data_glom$Phylum, Abundance = round(data_glom$Abundance,3)*100)
+df = df[df$Phylum!="< 3% abundancia",]
+df<-df[ order(df$Treatment,df$Phylum),]
+mean<-tapply(df$Abundance, list(df$Phylum,df$Treatment),mean)
+sd<-tapply(df$Abundance, list(df$Phylum,df$Treatment),sd)
+sink("mean_phylum.txt")
+print(mean)
+sink()
+sink("sd_phylum.txt")
+print(sd)
+sink()
+```
+## Class barplot
+```{r}
+subset = biomfile_merged
+rel.abun = transform_sample_counts(subset, function(x) x / sum(x))
+glom <- tax_glom(rel.abun, taxrank = 'Class')
+data_glom<- psmelt(glom) 
+data_glom$Class <- as.character(data_glom$Class) 
+data_glom$Class[data_glom$Abundance < 0.03] <- "< 3% abundance"
+data_glom$Class[data_glom$Class == "unidentified"] <- "Not classified"
+data_glom$Class[data_glom$Class == "undefined"] <-"Not classified"
+
+data_glom$Lenticel_disease_status[data_glom$Lenticel_disease_status == "Necrotic"] <-"Severe"
+data_glom$Lenticel_disease_status[data_glom$Lenticel_disease_status == "Healthy"] <-"Mild"
+
+plot_colors <- c( "palegoldenrod","gray40","thistle1", "lightsteelblue","darkseagreen1",
+                   "#CBD588", "plum4", "#652926","Khaki4", "yellow3", "cadetblue3",
+                   "lightsteelblue3", "honeydew3",
+
+                  "gray80", "yellow2", "slateblue1", "#5F7FC7","#DA5724", "#8A7C64",
+                  "gray30", "#508578", "#CD9BCD", "gray80","#AD6F3B",
+                  "darkseagreen4","deepskyblue1","gray50" , "yellow2", "slateblue1",
+                  "#673770","thistle4","yellow4",
+                   "#5E738F", "#8A7C64","gray30", "lightpink3")
+
+Class <- ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Class, Abundance)))+
+  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors) +
+  ylab("Relative abundance") + xlab("") +
+  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
+        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
+        axis.line = element_line(colour = "black"),
+        axis.ticks = element_line(colour = "black"),
+        axis.title.y = element_text(face="plain", colour="black", size=13,family="serif"),
+        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=13,family="serif"),
+        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=13,family="serif"),
+        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
+        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
+  theme(legend.title = element_blank(),legend.text = element_text(family="serif",size=12))+
+  theme(strip.text.x = element_text(size = 13 , family = 'serif'))
+
+print(Class)
+
+df = data.frame(Treatment = data_glom$Farm, Class = data_glom$Class, Abundance = round(data_glom$Abundance,3)*100)
+df = df[df$Class!="< 3% abundancia",]
+df<-df[ order(df$Treatment,df$Class),]
+mean<-tapply(df$Abundance, list(df$Class,df$Treatment),mean)
+sd<-tapply(df$Abundance, list(df$Class,df$Treatment),sd)
+sink("mean_Class.txt")
+print(mean)
+sink()
+sink("sd_Class.txt")
+print(sd)
+sink()
+```
+```{r}
+
+Phylum <- Phylum + theme(legend.key.height= unit(0.2, 'cm'),
+        legend.key.width= unit(0.2, 'cm'))
+
+Class <- Class + theme(legend.key.height= unit(0.2, 'cm'),
+        legend.key.width= unit(0.2, 'cm'))
+
+po<-ggarrange(ggarrange(Phylum+labs(tag= "A"),Class+labs(tag= "B"), nrow= 2)) 
+po
+ggsave("Fig4.jpg",plot=po,dpi = 300,width = 6,height = 8,units = c("in"))
+
+```
+
+### diferential abundance analysis
+
+loading the data for diferencial abundance annalysis-Escondida
+
+```{r escondida diferential abundance, message=FALSE, warning=FALSE}
+
+biomfile <- import_biom("ASVs_enrich_Escondida.biom")
+biomfile_mapfile <- import_qiime_sample_data("metadata_real1.txt")
+tree <- read_tree("tree.nwk")
+biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
+colnames(tax_table(biomfile_merged)) <- c( "Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
+sam <-sample_data(biomfile_merged)
+otu.table <- otu_table(biomfile_merged)
+
+otu.table<-otu.table[!(otu.table[,1]<0.005&otu.table[,2]<0.005),]
+#over 0.5%
+taxa <- tax_table(biomfile_merged)
+otutax = phyloseq(otu.table, taxa)
+GP.chl = merge_phyloseq(otutax, sam, tree)
+
+```
+
+```{r making a df}
+
+labels_new<-c("ASV22_Not_classified", "ASV57_g_Erythrobasidium", "ASV31_c_Cystobasidiomycetes", 
+              "ASV30_g_Cystobasidium", "ASV53_g_Golubevia", "ASV25_g_Meira", "ASV75_g_Vishniacozyma",
+              "ASV11_g_Vishniacozyma", "ASV15_g_Vishniacozyma", "ASV24_g_Setophoma","ASV34_g_Bacidina",
+              "ASV18_g_Bacidina", "ASV6_g_Hyphozyma",  "ASV4_g_Cladosporium",  "ASV1_Not_classified",
+              "ASV2_Not_classified",  "ASV12_Not_classified", "ASV3_Not_classified", "ASV7_Not_classified",
+              "ASV42_Not_classified", "ASV41_Not_classified", "ASV60_g_Neodevriesia", "ASV9_Not_classified",
+              "ASV10_o_Chaetothyriales", "ASV13_Not_classified")
+
+tree_new<-phy_tree(GP.chl)
+tree_new$tip.label<-labels_new
+otu_table_new<-otu_table(GP.chl)
+row.names(otu_table_new)<-labels_new
+taxa_new<-tax_table(GP.chl)
+row.names(taxa_new)<-labels_new
+sample_data_new<-sample_data(GP.chl)
+otutax_new = phyloseq(otu_table_new, taxa_new)
+merge_new = merge_phyloseq(otutax_new, sample_data_new, tree_new)
+
+df<- as.data.frame(otu_table_new)
+df$Ratio <- df$Escondida_Severo/df$Escondida_Leve
+df$ASVs<- phy_tree(tree_new)$tip.label
+df$Enriched_in[df$Ratio < 1]<- "Mildly damaged fruits"
+df$Enriched_in[df$Ratio >= 1]<- "Severely damaged fruits"
+
+df1 <- data.frame(
+  ASVs = phy_tree(tree_new)$tip.label, Ratio = df$Ratio, Enriched_in = df$Enriched_in 
+)
+
+df_anotations <- data.frame(node = c(1,28,35), 
+                            taxa = c("Not lassified", "Basidiomycetes", "Ascomycetes"))
+
+df_anotations_class <- data.frame(node = c(41,23,49,38,13,10,30,32,33,1), 
+                                  Class = c("Dothideomycetes", "Not classified", "Eurotiomycetes", "Lecanoromycetes", 
+                                            "Leotiomycetes", "Dothideomycetes", "Cystobasidiomycetes","Exobasidiomycetes",
+                                            "Tremellomycetes", "Not classified"))
+
+df_anotations_class$Class <- factor(df_anotations_class$Class, 
+                                    levels = c("Dothideomycetes", "Not classified", "Eurotiomycetes", 
+                                               "Lecanoromycetes", "Leotiomycetes", "Cystobasidiomycetes",
+                                               "Exobasidiomycetes","Tremellomycetes"))
+#p + geom_text(aes(label=node), hjust=-.3)
+
+```
+## Escondida plot
+
+*Fig 6.* Taxonomy and relative abundance of the amplicon sequence variants (ASVs) enriched (p-value < 0.05) in the fungal communities of avocado cv.
+Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida during the traviesa harvest of 2020.
+Shown are the taxonomic relation (A) and the relative abundances (B) of the ASVs group by color according to the clade (Supplementary Table 5).
+
+```{r ploting the data}
+
+p <- ggtree(tree_new) + geom_tiplab(align=T, size=3) + xlim(-.1, 3)+ hexpand(.01)+ labs(tag = "A")
+
+p <- p + geom_hilight(data=df_anotations_class, aes(node=node, fill=Class),  alpha=0.2,  extend=3, type = "roundrect")
+p<-p+geom_nodepoint(aes(subset = node == 35, x = x - .07),size = 3, colour = 'brown3', shape = 19)
+p<-p+geom_nodepoint(aes(subset = node == 28, x = x - 0.12),size = 3, colour = 'deepskyblue3', shape = 19)
+p<- p +   theme(legend.title = element_text(family="serif",size=12, face = "bold"),legend.text = element_text(family="serif",size=10))
+
+p1 <- ggplot(df1, aes(x = ASVs, y = log10(Ratio))) + geom_col(aes(fill=Enriched_in)) + theme_classic() + coord_flip() + labs(tag = "B")
+p1 <- p1 + scale_fill_manual("Enriched in:",values= alpha(c("Mildly damaged fruits" = "#00A087B2", "Severely damaged fruits" ="#7E6148B2"),0.4))
+p1 <- p1 + ylab("log10(Abundance severe/Abundance mild)") + xlab("") + guides(y = "none") + theme(axis.text.y=element_blank(),axis.ticks.y=element_blank())
+p1<- p1+  theme(axis.title.x = element_text(face="plain", colour="black", size=11,family="serif"),
+        axis.text.x  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif")) +
+  theme(legend.title = element_text(family="serif",size=12, face = "bold"),legend.text = element_text(family="serif",size=10))
+
+po <- p1 %>% insert_left(p)
+
+#####
+
+data <- data.frame(Xdata = rnorm(2), Ydata = rnorm(2),Phylum =c("Ascomycete","Basidiomycete"))
+
+gplot <- ggplot(data, aes(Xdata, Ydata, color = Phylum)) + geom_point(size = 3) +scale_color_manual(values = c("Ascomycete" = "brown3", "Basidiomycete" = "deepskyblue3"))
+gplot <- gplot +   theme(legend.title = element_text(family="serif",size=12, face = "bold"),legend.text = element_text(family="serif",size=10),legend.key = element_rect(colour = NA, fill = NA))
+
+jpeg("Fig5.jpg",width = 8,height = 6,units = c("in"), res=300) 
+po
+leg=g_legend(gplot)
+wc_table_vp <- viewport(x = 0.74, y = 0.20, just = c("left", "top"),height = 0.1, width = 0.2)
+pushViewport(wc_table_vp)
+grid.draw(leg)
+
+dev.off()
+
+```
+
+loading the data for diferencial abundance annalysis-Sinai
+
+```{r Sinai diferential abundance, message=FALSE, warning=FALSE, paged.print=FALSE}
+
+# biomfile <- import_biom("ASVs_enrich_Sinai.biom")
+
+#biomfile_mapfile <- import_qiime_sample_data("metadata_real1.txt")
+#tree <- read_tree("tree.nwk")
+biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
+colnames(tax_table(biomfile_merged)) <- c( "Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
+sam <-sample_data(biomfile_merged)
+otu.table <- otu_table(biomfile_merged)
+
+otu.table<-otu.table[!(otu.table[,1]<0.005&otu.table[,2]<0.005),]
+#over 0.5%
+taxa <- tax_table(biomfile_merged)
+otutax = phyloseq(otu.table, taxa)
+GP.chl = merge_phyloseq(otutax, sam, tree)
+
+```
+
+```{r making a df sinai}
+
+labels_new<-c("ASV37_Not_classified", "ASV96_Not_classified","ASV33_g_Symmetrospora","ASV20_g_Symmetrospora","ASV31_c_Cystobasidiomycetes",
+              "ASV54_c_Cystobasidiomycetes","ASV11_g_Vishniacozyma","ASV65_g_Colletotrichum", "ASV40_g_Geastrumia", "ASV14_g_Pseudocercospora", 
+              "ASV4_g_Cladosporium",  "ASV2_Not_classified",  "ASV3_Not_classified",  "ASV7_Not_classified",  "ASV70_Not_classified",
+              "ASV10_o_Chaetothyriales", "ASV13Not_classified", "ASV26_g_Aureobasidium")
+
+tree_new<-phy_tree(GP.chl)
+tree_new$tip.label<-labels_new
+otu_table_new<-otu_table(GP.chl)
+row.names(otu_table_new)<-labels_new
+taxa_new<-tax_table(GP.chl)
+row.names(taxa_new)<-labels_new
+sample_data_new<-sample_data(GP.chl)
+otutax_new = phyloseq(otu_table_new, taxa_new)
+merge_new = merge_phyloseq(otutax_new, sample_data_new, tree_new)
+
+df<- as.data.frame(otu_table_new)
+df$Ratio <- df$Sinai_Severo/df$Sinai_Leve
+df$ASVs<- phy_tree(tree_new)$tip.label
+df$Enriched_in[df$Ratio < 1]<- "Mildly damaged fruits"
+df$Enriched_in[df$Ratio >= 1]<- "Severely damaged fruits"
+
+df1 <- data.frame(
+  ASVs = phy_tree(tree_new)$tip.label, Ratio = df$Ratio, Enriched_in = df$Enriched_in 
+)
+
+df_anotations <- data.frame(node = c(20,22,26), 
+                            taxa = c("Not lassified", "Basidiomycetes", "Ascomycetes"))
+
+df_anotations_class <- data.frame(node = c(20,7,23,
+                                           8, 18,9, 35, 30), 
+                                  Class = c("Not classified","Tremellomycetes", "Cystobasidiomycetes",
+                                            "Sordariomycetes", "Dothideomycetes" ,"Dothideomycetes", 
+                                            "Eurotiomycetes","Dothideomycetes"))
+
+df_anotations_class$Class <- factor(df_anotations_class$Class, 
+                                    levels = c("Dothideomycetes", "Eurotiomycetes","Sordariomycetes", 
+                                               "Cystobasidiomycetes","Tremellomycetes","Not classified"))
+#p + geom_text(aes(label=node), hjust=-.3)
+
+```
+*Fig 7.* Taxonomy and relative abundance of the amplicon sequence variants (ASVs) enriched (p- value < 0.05) in the fungal communities of avocado cv.
+Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Sinai during the traviesa harvest of 2020.
+Shown are the taxonomic relation (A) and the relative abundances (B) of the ASVs group by color according to the clade (Supplementary Table 6).
+
+```{r ploting the Sinai}
+
+p <- ggtree(tree_new) + geom_tiplab(align=T, size=3) + xlim(-.1, 3)+ hexpand(.01)+ labs(tag = "A")
+
+p <- p + geom_hilight(data=df_anotations_class, aes(node=node, fill=Class),  alpha=0.2,  extend=3, type = "roundrect")
+p<-p+geom_nodepoint(aes(subset = node == 26, x = x - .13),size = 3, colour = 'brown3', shape = 19)
+p<-p+geom_nodepoint(aes(subset = node == 22, x = x - 0.124),size = 3, colour = 'deepskyblue3', shape = 19)
+p<- p +   theme(legend.title = element_text(family="serif",size=12, face = "bold"),legend.text = element_text(family="serif",size=10))
+
+p1 <- ggplot(df1, aes(x = ASVs, y = log10(Ratio))) + geom_col(aes(fill=Enriched_in)) + theme_classic() + coord_flip() + labs(tag = "B")
+p1 <- p1 + scale_fill_manual("Enriched in:",values= alpha(c("Mildly damaged fruits" = "#00A087B2", "Severely damaged fruits" ="#7E6148B2"),0.4))
+p1 <- p1 + ylab("log10(Abundance severe/Abundance mild)") + xlab("") + guides(y = "none") + theme(axis.text.y=element_blank(),axis.ticks.y=element_blank())
+p1<- p1+  theme(axis.title.x = element_text(face="plain", colour="black", size=11,family="serif"),
+        axis.text.x  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif")) +
+  theme(legend.title = element_text(family="serif",size=12, face = "bold"),legend.text = element_text(family="serif",size=10))
+
+po <- p1 %>% insert_left(p)
+
+jpeg("Fig6.jpg",width = 8,height = 6,units = c("in"), res=300) 
+po
+leg=g_legend(gplot)
+wc_table_vp <- viewport(x = 0.74, y = 0.20, just = c("left", "top"),height = 0.1, width = 0.2)
+pushViewport(wc_table_vp)
+grid.draw(leg)
+
+dev.off()
+
+ggsave("Fig6.jpg",plot=po,dpi = 300,width = 8,height = 6,units = c("in"))
 ```
@@
         panel.background = element_rect(fill = "white", colour = "black", linetype = 1, size = 0.5),
-        panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=11,family = "serif"), plot.margin = margin(1, 0.6, 1, 1, "cm"))  +
-  scale_colour_manual(values=c("gray85","gray65","gray85","gray65"),labels = c("Escondida_Mild","Escondida_Severe", "Sinai_Mild","Sinai_Severe"))+  
+        panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=10,family = "serif"), plot.margin = margin(1, 0.5, 1, 1, "cm"))  +
+  scale_colour_manual(values=c("gray85","gray55","gray85","gray55"),labels = c("Escondida_Mild","Escondida_Severe", "Sinai_Mild","Sinai_Severe"))+  
   stat_ellipse(type = "t", size=0.5) + theme(legend.position = "bottom") +
-  labs(x = "PCoA (60.4%)", y= "PCoA (12.2%)")
+  labs(x = "PCoA (60.4%)", y= "PCoA (12.2%)")+ guides(colour = guide_legend(order = 2), 
+              shape = guide_legend(order = 1))
 legend <- get_legend(PCoA)
@@
 ```
-
-###CAP
-
-```{r CAP}
-agricultural.ord<- ordinate(merge2, "CAP", "wunifrac", ~Farm)
-
-agricultural_plot<- plot_ordination(merge2, agricultural.ord, type = "sites",
-                                    color = "Farm",
-                                    title = "", label = NULL)
-
-CAP = agricultural_plot  +
-  geom_point(aes(color =Farm,shape = Farm1), size = 3) +
-  theme(panel.grid.major = element_blank(), 
-        panel.grid.minor = element_blank(), 
-        rect = element_rect(fill = "white", colour = "black",size = 0.5, linetype = 1),
-        axis.ticks = element_line(colour = "black"),
-        axis.title.x = element_text(face="plain",family = "serif", colour="black", size=12),
-        axis.title.y = element_text(face="plain",family = "serif", colour="black", size=12),
-        axis.text.x  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
-        axis.text.y  = element_text(face="plain",family = "serif", colour = "black", angle=360, vjust=0.5, size=10),
-        panel.background = element_rect(fill = "white", colour = "black", linetype = 1, size = 0.5),
-        panel.border = element_blank(), legend.title = element_blank(), legend.text=element_text(size=11,family = "serif"), plot.margin = margin(0.71, 1, 1, 0.6, "cm"))  +
-  scale_colour_manual(values=c("gray85","gray65","gray85","gray65"),labels =
-                        c("Escondida_Mild","Escondida_Severe",
-                          "Sinai_Mild","Sinai_Severe")) + 
-  stat_ellipse(type = "t", size=0.5) + labs(x = "CAP (23.7%)", y= "CAP (45.8%)")+theme(legend.position = "none")
-
-```
-*Fig 4.* Fungal communities’ structure for fruits of avocado cv.
-Hass fruits with different severities of lenticel damage (Mild and Severe) collected from the La Escondida and El Sinai farms during the traviesa harvest of 2020.
-Cumulative sum scaling (CSS) transformed reads were used to calculate weighted unifrac distance.
-Shown are the bidimensional planes of the principal coordinates analysis (PCoA) (72.6 % of the overall variance) (A) and canonical analysis of principal coordinates (CAP) constrained by the farm (La Escondida and El Sinai) (68.8 % of the overall variance; p-value: 0.001) (B).
-Each point represents the fungal community of a fruit, and the colors show the origin (La Escondida o El Sinai) and damage severity (Severe or Mild) of the fruit.
-The ellipsis are the 95 % confidence level ellipses.
-
-```{r PCoA and PCA plots}
-
-po<-grid.arrange(PCoA+labs(tag = "A"),CAP+labs(tag = "B"),legend, ncol=2,nrow = 2, 
-             layout_matrix = rbind(c(1,2), c(3,3)),
-             widths = c(2.7, 2.7), heights = c(2.5, 0.2))
-```
-## Taxonomy bat plots
-Loading the ASVs table
-
-```{r data barplot}
-biomfile <- import_biom(paste(path,"/ASVs_table9_dada2R.biom",sep=""))
-biomfile_mapfile <- import_qiime_sample_data(paste(path,"/metadata_real.txt",sep=""))
-biomfile_merged <- merge_phyloseq(biomfile,biomfile_mapfile)
-colnames(tax_table(biomfile_merged)) <- c("Domain", "Phylum", "Class", "Order", "Family", "Genus", "Species")
-#sample_data(biomfile_merged)
-
-plot_colors <- c( "palegoldenrod","gray90", "plum4", "lightsteelblue","darkseagreen1",
-                   "darkseagreen4","deepskyblue1","gray50" , "yellow2", "slateblue1",
-                   "#CBD588", "#5F7FC7","#DA5724", "#508578", "#CD9BCD", "#AD6F3B",
-                   "#673770","Khaki4", "#652926", "yellow3", "cadetblue3",
-                   "lightsteelblue3", "honeydew3", "gray80","thistle4","yellow4",
-                   "#5E738F", "#8A7C64","gray30", "lightpink3")
-```
-
-## Phylum barplot
-
-```{r}
-subset = biomfile_merged
-rel.abun = transform_sample_counts(subset, function(x) x / sum(x))
-glom <- tax_glom(rel.abun, taxrank = 'Phylum')
-data_glom<- psmelt(glom) 
-data_glom$Phylum <- as.character(data_glom$Phylum) 
-data_glom$Phylum[data_glom$Abundance < 0.03] <- "< 3% abundancia"
-data_glom$Phylum[data_glom$Phylum == "unidentified"] <- "Not classified"
-data_glom$Phylum[data_glom$Phylum == "undefined"] <-"Not classified"
-
-p1 <- ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Phylum, Abundance)))+
-  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors) +
-  ylab("Relative abundance") + xlab("") +
-  theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
-        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
-        axis.line = element_line(colour = "black"),
-        axis.ticks = element_line(colour = "black"),
-        axis.title.y = element_text(face="plain", colour="black", size=14,family="serif"),
-        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=10,family="serif"),
-        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif"),
-        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
-        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  theme(legend.title = element_blank(),legend.text = element_text(family="serif",size=10)) + 
-  theme(strip.text.x = element_text(size = 12 , family = 'serif'))
-
-```
-
-```{r Barplot Ascomycota }
-
-subset = subset_taxa(biomfile_merged, Phylum == "Ascomycota")
-
-rel.abun = transform_sample_counts(subset, function(x) x / sum(x) )
-glom <- tax_glom(rel.abun, taxrank = 'Genus')
-data_glom<- psmelt(glom)
-data_glom$Genus <- as.character(data_glom$Genus)
-
-data_glom$Genus[data_glom$Abundance < 0.03] <- "< 3% abundancia"
-data_glom$Genus[data_glom$Genus == "unidentified"] <- "Not classified"
-data_glom$Genus[data_glom$Genus == "undefined"] <-"Not classified"
-
-p2<-ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Genus, Abundance)))+
-  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors, name ="Genus") +
-  ylab("Relative abundance") + xlab("") +
-   theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
-        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
-        axis.line = element_line(colour = "black"),
-        axis.ticks = element_line(colour = "black"),
-        axis.title.y = element_text(face="plain", colour="black", size=14,family="serif"),
-        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=10,family="serif"),
-        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif"),
-        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
-        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  theme(legend.title = element_text(family="serif",size=12),legend.text = element_text(family="serif",size=10)) +
-  theme(strip.text.x = element_text(size = 12 , family = 'serif'))
-
-```
-
-```{r Basidiomycota}
-subset = subset_taxa(biomfile_merged, Phylum == "Basidiomycota")
-
-rel.abun = transform_sample_counts(subset, function(x) x / sum(x) )
-glom <- tax_glom(rel.abun, taxrank = 'Genus')
-data_glom<- psmelt(glom)
-data_glom$Genus <- as.character(data_glom$Genus)
-
-data_glom$Genus[data_glom$Abundance < 0.03] <- "< 3% abundancia"
-data_glom$Genus[data_glom$Genus == "unidentified"] <- "Not classified"
-data_glom$Genus[data_glom$Genus == "undefined"] <-"Not classified"
-
-p3<-ggplot(data_glom, aes(x = Lenticel_disease_status, y = Abundance/6, fill = reorder(Genus, Abundance)))+
-  geom_bar(stat = "identity") + facet_wrap(~Farm1) + scale_fill_manual(values =plot_colors, name ="Genus") +
-  ylab("Relative abundance") + xlab("")  +
-    theme(panel.grid.major = element_blank(), panel.grid.minor = element_blank(), 
-        rect = element_rect(fill = "white",  colour = "black",  size = 0.5, linetype = 1),
-        axis.line = element_line(colour = "black"),
-        axis.ticks = element_line(colour = "black"),
-        axis.title.y = element_text(face="plain", colour="black", size=14,family="serif"),
-        axis.text.x  = element_text(face="plain", colour = "black", angle=30, vjust=0.6, size=10,family="serif"),
-        axis.text.y  = element_text(face="plain",colour = "black", angle=360, vjust=0.5, size=10,family="serif"),
-        panel.background = element_rect(fill = "white", colour = "white", linetype = 1, size = 0.5),
-        panel.border = element_blank()) + scale_y_continuous(labels = percent_format(accuracy = 1)) +
-  theme(legend.title = element_text(family="serif",size=12),legend.text = element_text(family="serif",size=10)) +
-  theme(strip.text.x = element_text(size = 12 , family = 'serif'))
-
-```
-
-```{r}
-#po<-ggarrange(p1,ggarrange(p2, p3, nrow = 2), ncol = 2    , widths = c(0.78,1))
-
-p1 <- p1 + theme(legend.key.height= unit(0.2, 'cm'),
-        legend.key.width= unit(0.2, 'cm'))
-
-p2 <- p2 + theme(legend.key.height= unit(0.2, 'cm'),
-        legend.key.width= unit(0.2, 'cm'))
-
-p3 <- p3 + theme(legend.key.height= unit(0.2, 'cm'),
-        legend.key.width= unit(0.2, 'cm'))
-
-po<-grid.arrange(p1+labs(tag= "A"),p3+labs(tag = "B"),p2+labs(tag = "C"), ncol=1,nrow = 3)
-
-p2/p3 
-```

### 2023-04-01 R/Principal_lentcelosisa.Rmd
before last revision

---
title: "Principal_analysis_lenticelosis"
author: "dru"
output: html_document
date: "2022-08-16"
---

## Preparing the environment

Loading required Packages

```{r Packages, echo=TRUE, message=FALSE, warning=FALSE}

library(glmmTMB)
library(bbmle)
library(DHARMa)
library(readxl)
library(tidyverse)

```

## Loading and inspecting the data

Loading and inspecting the file 'Lenticel_Damage_Summary_All_Harvest.xlsx'. This file has two-years of lenticel damage measurements recorded in two avocado farms across four harvest.

```{r echo=TRUE, message=FALSE, warning=FALSE}
Lenticel_file <- read_excel("C:/Users/Dru/Desktop/Cartama_paper/files/Lenticel_Damage_Summary_All_Harvest.xlsx")
glimpse(Lenticel_file)
```

Checking for NA, miss speels and anomalies in the data:

```{r inspecting}

table(Lenticel_file$Cosecha)
table(Lenticel_file$UP)

f <-subset(Lenticel_file,Lenticel_file$UP=="Escondida")
f1 <- subset(Lenticel_file,Lenticel_file$UP=="Sinai")
table(f$Lote)
table(f$Arbol)
table(f1$Lote)
table(f1$Arbol)
summary(Lenticel_file$Severidad_0)
summary(Lenticel_file$Severidad_1)
summary(Lenticel_file$Incidencia_0)
summary(Lenticel_file$Incidencia_1)
```

Problems:

* Some tree numbers are shared between La Escondida y El Sinai, and this redundancy can result in problems during the analysis.
* Lenticel damage columns have several NA. Fruits having NA the severidad_0 or incidence_0 were removed from all the analyses, and those having NA in severidad_1 or incidence_1 only from the analysis evaluating disease progresion

## Cleaning and preparing the data
### cleaning actions:

* The columns cosecha, Año, Severidad_pedunculo, arbol and the last three empty columns were removed as they are not used during the analysis
* The 'p' simbol in the column Cosecha is changed for 'm' to especify the main harvest.
* Generated a column Tree which has the name of the tree indicated by the farm and tree number (i.e., Sinai15) to avoid problems during the analysis

```{r cleaning}
Lenticel_file$...13<-NULL
Lenticel_file$...14<-NULL
Lenticel_file$...15<-NULL
Lenticel_file$Año<-NULL
Lenticel_file$cosecha<-NULL
Lenticel_file$Severidad_pedunculo<-NULL
Lenticel_file[Lenticel_file=="2019_p"]<-"2019_m"
Lenticel_file[Lenticel_file=="2020_p"]<-"2020_m"
Lenticel_file$Tree<-paste(Lenticel_file$UP,Lenticel_file$Arbol,sep="")
Lenticel_file$Arbol<-NULL

df <- Lenticel_file %>% drop_na(Severidad_0 , Incidencia_0)
colnames(df)[which(names(df) == "Cosecha")] <- "Harvest"
colnames(df)[which(names(df) == "UP")] <- "Farm"
colnames(df)[which(names(df) == "Lote")] <- "Plot"
colnames(df)[which(names(df) == "Fruta")] <- "Fruit"
colnames(df)[which(names(df) == "Severidad_0")] <- "Sev_0dph"
colnames(df)[which(names(df) == "Severidad_1")] <- "Sev_21dph"
colnames(df)[which(names(df) == "Incidencia_0")] <- "Inc_0dph"
colnames(df)[which(names(df) == "Incidencia_1")] <- "Inc_21dph"
df$Inc_ratio <- df$Inc_21dph-df$Inc_0dph
df$Sev_ratio <- df$Sev_21dph-df$Sev_0dph
glimpse(df)
summary(df$Sev_0dph)

#Datos_mat<-subset(Datos_mat,Datos_mat$Cosecha!="2020_t")

plot<-factor(df$Plot)
tree<-factor(df$Tree)
farm<-factor(df$Farm)
fpt<-farm:plot:tree
fp<-farm:plot
pt<- plot:tree
year<-factor(df$Harvest)
fruta<-factor(df$Fruit)
```
# 0dph annalysis for the severity and Incidence
## Building the severity models
We are using zero-inflated generalized linear mixed models for assessing differences in severity between farms and harvests. We are using glmmTMB function of the glmmTMB package with the beta family().
https://cran.r-project.org/web/packages/glmmTMB/vignettes/glmmTMB.pdf

```{r}

y<-df$Sev_0dph/100

modelo <- glmmTMB(y~farm*year +  (1|fp) + (1|fpt),ziformula=~1,family=beta_family())

modelo1 <- glmmTMB(y~farm*year + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=beta_family())
#modelo1 <- glmmTMB(y~farm+year + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=beta_family())
#modelo2 <- glmmTMB(y~year + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=beta_family())
#modelo3 <- glmmTMB(y~farm + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=beta_family())

```
## Testing the model
Testing the good-of-fit of the model with the DHARMA library
https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html

We used AIC model selection to distinguish among a set of possible models describing the relationship between farm and harvest and severity. The best-fit model, carrying 100% of the cumulative model weight, included every parameter with the interaction effects.
https://www.scribbr.com/statistics/akaike-information-criterion/#:~:text=The%20Akaike%20information%20criterion%20(AIC,best%20fit%20for%20the%20data.

```{r}

#AICtab(modelo,modelo1,modelo2,modelo3, base=TRUE,weights = TRUE)

residual_simulation<-simulateResiduals(modelo)
plot(residual_simulation)
residual_simulation_years <-recalculateResiduals(residual_simulation, group = df$Tree)
plot(residual_simulation_years)
testDispersion(residual_simulation)
testZeroInflation(residual_simulation)
testCategorical(residual_simulation, catPred = df$Tree)
par(mfrow = c(1,2))
plotResiduals(residual_simulation, farm)
plotResiduals(residual_simulation, year)

sink("Sev_0h.txt")
print(summary(modelo))
sink()
```

## Building the incidence models
We are using zero-inflated generalized linear mixed models for assessing differences between farms and years.  we are using glmmTMB function of the glmmTMB package with the negative binomial family.
https://cran.r-project.org/web/packages/glmmTMB/vignettes/glmmTMB.pdf

```{r}

y<-round(df$Inc_0dph)

modelo <- glmmTMB(y~farm*year + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=nbinom2)
modelo1 <- glmmTMB(y~farm+year + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=nbinom2)
modelo2 <- glmmTMB(y~year + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=nbinom2)
modelo3 <- glmmTMB(y~farm + (1|farm) + (1|fp) + (1|fpt),ziformula=~1,family=nbinom2)

```
## Testing the model
Testing the model with the DHARMA library
https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html
We selected modelo1 as its better fitted and the AIC penalty is low. We are having issues with no homogen variance between harvest. We also have a small deviation from the expected distributions of the residualas

```{r}

AICtab(modelo,modelo1,modelo2,modelo3, base=TRUE)

residual_simulation<-simulateResiduals(modelo)
plot(residual_simulation)
residual_simulation_years <-recalculateResiduals(residual_simulation, group = df$Tree)
plot(residual_simulation_years)
testDispersion(residual_simulation)
testZeroInflation(residual_simulation)
#testCategorical(residual_simulation, catPred = df$Tree)
par(mfrow = c(1,2))
plotResiduals(residual_simulation, farm)
plotResiduals(residual_simulation, year)

sink("In_0h.txt")
print(summary(modelo))
sink()
```
# 21dph annalysis for the severity and Incidence
## Building the severity models
We are using zero-inflated generalized linear mixed models for assessing differences in severity between time points (0dph and 21dph) and harvests. These evlauations were mede for each farm separately using glmmTMB function of the glmmTMB package with the beta family().
https://cran.r-project.org/web/packages/glmmTMB/vignettes/glmmTMB.pdf

```{r}
dfe<-na.omit(subset(df,df$Farm=="Escondida"))
dfs<-na.omit(subset(df,df$Farm=="Sinai"))
df1<-na.omit(df)
y<-c(df1$Sev_0dph,df1$Sev_21dph)/100
ye<-c(dfe$Sev_0dph,dfe$Sev_21dph)/100
ys<-c(dfs$Sev_0dph,dfs$Sev_21dph)/100

time<-factor(c(rep("0dpc",length(y)/2),rep("21dpc",length(y)/2)))
timee<-factor(c(rep("0dpc",length(ye)/2),rep("21dpc",length(ye)/2)))
times<-factor(c(rep("0dpc",length(ys)/2),rep("21dpc",length(ys)/2)))

farm<-c(df1$Farm,df1$Farm)
f<-factor(c(df1$Fruit,df1$Fruit))
h<-factor(c(df1$Harvest,df1$Harvest))

fe<-factor(c(dfe$Fruit,dfe$Fruit))
he<-factor(c(dfe$Harvest,dfe$Harvest))
fs<-factor(c(dfs$Fruit,dfs$Fruit))
hs<-factor(c(dfs$Harvest,dfs$Harvest))

modelo <- glmmTMB(y ~ time * h *farm + (1|f)  ,ziformula= ~ 1,family=beta_family())
modelos <- glmmTMB(ys ~ times * hs + (1|fs) ,ziformula= ~ 1,family=beta_family())
modeloe <- glmmTMB(ye ~ timee * he + (1|fe) ,ziformula= ~ he + timee,family=beta_family())
```
## Testing the model
Testing the model with the DHARMA library
https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html
We selected modelos and modeloe

```{r}
#modelo <- glmmTMB(y ~ time * h *farm + (1|f)  ,ziformula= ~ 1,family=beta_family())
#modelo1 <-glmmTMB(y ~ time * h +farm + (1|f)  ,ziformula= ~ 1,family=beta_family()) 
#modelo2 <- glmmTMB(y ~ time + h *farm + (1|f)  ,ziformula= ~ 1,family=beta_family())
#modelo3 <- glmmTMB(y ~ time + h +farm + (1|f)  ,ziformula= ~ 1,family=beta_family())

AICtab(modelo,modelo1,modelo2,modelo3, base=TRUE,weights = TRUE)

residual_simulation<-simulateResiduals(modelo)
plot(residual_simulation)
testDispersion(residual_simulation)
testZeroInflation(residual_simulation)
par(mfrow = c(1,2))
plotResiduals(residual_simulation, h)

```
```{r}
dfe<-na.omit(subset(df,df$Farm=="Escondida"))
dfs<-na.omit(subset(df,df$Farm=="Sinai"))
df1<-na.omit(df)
y<-round(c(df1$Sev_0dph,df1$Sev_21dph))
ye<-round(c(dfe$Inc_0dph,dfe$Inc_21dph))
ys<-round(c(dfs$Inc_0dph,dfs$Inc_21dph))

time<-factor(c(rep("0dpc",length(y)/2),rep("21dpc",length(y)/2)))
timee<-factor(c(rep("0dpc",length(ye)/2),rep("21dpc",length(ye)/2)))
times<-factor(c(rep("0dpc",length(ys)/2),rep("21dpc",length(ys)/2)))

farm<-c(df1$Farm,df1$Farm)
f<-factor(c(df1$Fruit,df1$Fruit))
h<-factor(c(df1$Harvest,df1$Harvest))

fe<-factor(c(dfe$Fruit,dfe$Fruit))
he<-factor(c(dfe$Harvest,dfe$Harvest))
fs<-factor(c(dfs$Fruit,dfs$Fruit))
hs<-factor(c(dfs$Harvest,dfs$Harvest))

#modelo <- glmmTMB(y ~ time * h *farm + (1|f)  ,ziformula= ~ 1,family=beta_family())
modelo <- glmmTMB(y ~ time * h *farm + (1|f)  ,ziformula= ~ 1,family=nbinom2)
modelo1 <-glmmTMB(y ~ time * h +farm + (1|f)  ,ziformula= ~ 1,family=nbinom2) 
modelo2 <- glmmTMB(y ~ time + h *farm + (1|f)  ,ziformula= ~ 1,family=nbinom2)
modelo3 <- glmmTMB(y ~ time + h +farm + (1|f)  ,ziformula= ~ 1,family=nbinom2)

#modeloe <- glmmTMB(ye ~ timee * he + (1|fe) ,ziformula= ~ 1 + timee,family=nbinom2)
```
## Testing the model
Testing the model with the DHARMA library
https://cran.r-project.org/web/packages/DHARMa/vignettes/DHARMa.html
We selected modelos and modeloe

```{r}
AICtab(modelo,modelo1,modelo2,modelo3, base=TRUE)
#modelos <- glmmTMB(ys ~ times * hs + (1|fs) ,ziformula= ~ 1,family=nbinom2)

residual_simulation<-simulateResiduals(modelo)
plot(residual_simulation)
testDispersion(residual_simulation)
testZeroInflation(residual_simulation)
plotResiduals(residual_simulation, h)

sink("In_0h_21h.txt")
print(summary(modelo))
sink()

```

```{r}

df1<-na.omit(df)

mat1<-data.frame(Farm =c(df1$Farm,df1$Farm), Time = factor(c(rep("0dpc",length(y)/2),rep("21dpc",length(y)/2))), 
                 Harvest = factor(c(df1$Harvest,df1$Harvest)), Severity = c(df1$Sev_0dph,df1$Sev_21dph)/100,
                 Incidence = round(c(df1$Inc_0dph,df1$Inc_0dph)), Fruit = c(df1$Fruit,df1$Fruit))

mat2 <-subset(mat1, mat1$Farm== "Sinai" & mat1$Harvest == "2020_m")
modelo <- glmmTMB(data=mat2, Severity ~ Time + (1|Fruit)  ,ziformula= ~ 1,family=beta_family())
residual_simulation<-simulateResiduals(modelo)
plot(residual_simulation)
testDispersion(residual_simulation)
summary(modelo)
modelo1 <- glmmTMB(data=mat2, Incidence ~ Time + (1|Fruit)  ,ziformula= ~ 1,family=poisson())
#modelo1 <- glmmTMB(data=mat2, Incidence ~ Time + (1|Fruit)  ,ziformula= ~ 1,family=nbinom2())
residual_simulation<-simulateResiduals(modelo1)
plot(residual_simulation)
testDispersion(residual_simulation)
summary(modelo1)

```

### 2023-04-01 severity-lenticelosis_macro/severity_lenticelosis.py

@@ -1,69 +1,0 @@
-#!/usr/bin/env python3
-# -*- coding: utf-8 -*-
-"""
-Created on Sat Aug 24 20:16:11 2019
-
-@author: druna
-"""
-#%%
-
-# para correr: python severity_lenticelosis.py 
-
-import csv
-import argparse
-import glob
-import os
-
-def compute_severity_lenticelosis(f_are_ind,f_are_tot):
-    with open(f_are_ind) as csvfile:
-        area_ind= csv.reader(csvfile, delimiter=',')
-        next(area_ind)    
-        area=0
-        ct=0
-        for row in area_ind:
-            ct=ct+1
-            area=area+float(row[1])
-        #print(area)    
-    with open(f_are_tot) as csvfile1:
-        area_tot= csv.reader(csvfile1, delimiter=',')        
-        next(area_tot)
-        for row in area_tot:
-            area_t=float(row[1])
-        #print(area_t)
-    severity=area/area_t*100
-    sev="%.2f" %severity
-
-    csvData = [sev,ct]
-    return(csvData)
-
-if __name__=="__main__":
-    parser = argparse.ArgumentParser(description='Process some integers.')
-    parser.add_argument('path', type=str, default="aguacates_1")
-    args = parser.parse_args()
-
-
-#    fieldnames = ['Imagen','Severity (%)', 'Incidence']
-#    writer = csv.DictWriter(csvfile, fieldnames=fieldnames)
-#
-#    writer.writeheader()
-#    writer.writerow({'first_name': 'Baked', 'last_name': 'Beans'})
-#    writer.writerow({'first_name': 'Lovely', 'last_name': 'Spam'})
-#    writer.writerow({'first_name': 'Wonderful', 'last_name': 'Spam'})
-
-    with open(args.path + "/output.csv", 'w') as csvFile:
-        writer = csv.writer(csvFile)
-        writer.writerow(['Imagen','Severity (%)', 'Incidence'])
-        
-        for f in glob.glob(args.path + "/*.txt"):
-            filename = f[:-4]
-            f_are_ind = filename + "_areas_ind.csv"
-            f_are_tot = filename + "_areas_tot.csv"
-        
-            if not (os.path.exists(f_are_ind) and os.path.exists(f_are_tot)):
-                csvData = [os.path.basename(filename), "##", "##"]
-                writer.writerow(csvData)
-                continue
-    
[…]
